---
title: "Compare R vs Rcpp"
author: "Yuxin Zou"
date: 2017-12-04
output: html_document
---

```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
knitr::read_chunk('../code/subset.data.R')
```

<!-- Update knitr chunk options -->
```{r knitr-opts-chunk, include=FALSE}
```

<!-- Insert the date the file was last updated -->
```{r last-updated, echo=FALSE, results='asis'}
```

<!-- Insert the code version (Git commit SHA1) if Git repository exists and R
 package git2r is installed -->
```{r code-version, echo=FALSE, results='asis'}
```

# Set up
```{r}
library(microbenchmark)
library(mashr)
```

## Equal S data
```{r}
set.seed(1)
simdata.equal1 = simple_sims(5000,5,0.5)
simdata.equal2 = simple_sims2(5000, 0.5)
simdata.equal = list(B = rbind(simdata.equal1$B, simdata.equal2$B), 
                     Bhat = rbind(simdata.equal1$Bhat, simdata.equal2$Bhat), 
                     Shat = rbind(simdata.equal1$Shat, simdata.equal2$Shat))
# data contains 4000 rows
data.equal = set_mash_data(simdata.equal$Bhat, simdata.equal$Shat, alpha=0)
U.c.equal = cov_canonical(data.equal)
# data driven
m.1by1 = mash_1by1(data.equal)
strong = get_significant_results(m.1by1,0.05)
# center Z
data.equal.Z = simdata.equal$Bhat/simdata.equal$Shat
data.center = set_mash_data(Bhat = apply(as.matrix(data.equal.Z), 2, function(x) x - mean(x)))
U.pca = cov_pca(data.center,5,strong)
U.e.equal = cov_ed(data.equal, U.pca, strong)
```

## Non-Equal S data
```{r}
set.seed(1)
simdata.diff1 = simple_sims(5000, 5, rep(c(0.5,0.4,0.1,1,0.2), 4000))
simdata.diff2 = simple_sims2(5000, rep(c(0.5,0.4,0.1,1,0.2), 4000))
simdata.diff = list(B = rbind(simdata.diff1$B, simdata.diff2$B), 
                    Bhat = rbind(simdata.diff1$Bhat, simdata.diff2$Bhat), 
                    Shat = rbind(simdata.diff1$Shat, simdata.diff2$Shat))
data.diff = set_mash_data(simdata.diff$Bhat, simdata.diff$Shat, alpha=0)
U.c.diff = cov_canonical(data.diff)
# data driven
m.1by1 = mash_1by1(data.diff)
strong = get_significant_results(m.1by1,0.05)
# center Z
data.diff.Z = simdata.diff$Bhat/simdata.diff$Shat
data.center = set_mash_data(Bhat = apply(as.matrix(data.diff.Z), 2, function(x) x - mean(x)))
U.pca = cov_pca(data.center,5,strong)
U.e.diff = cov_ed(data.diff, U.pca, strong)
```

# Compare likelihood

```{r}
library(assertthat)
source('~/Documents/GitHub/mashr-stephens/R/likelihoods_scaleddata.R')
source('~/Documents/GitHub/mashr-stephens/R/likelihoods_origdata.R')
source('~/Documents/GitHub/mashr-stephens/R/mash.R')
source('~/Documents/GitHub/mashr-stephens/R/compute_covs.R')
source('~/Documents/GitHub/mashr-stephens/R/RcppExports.R')
source('~/Documents/GitHub/mashr-stephens/R/set_data.R')
source('~/Documents/GitHub/mashr-stephens/R/opt.R')
source('~/Documents/GitHub/mashr-stephens/R/posterior.R')
source('~/Documents/GitHub/mashr-stephens/R/posterior_common_cov.R')
source('~/Documents/GitHub/mashr-stephens/R/posterior_lowmem.R')
```

```{r}
compute_likelihood = function(data, Ulist, algorithm.version=c('Rcpp','R')){
  algorithm.version = match.arg(algorithm.version)
  grid = autoselect_grid(data, sqrt(2))
  Ulist = normalize_Ulist(Ulist)
  xUlist = expand_cov(Ulist, grid, TRUE)
  J <- nrow(data$Bhat)
  P <- length(xUlist)
  lm <- calc_relative_lik_matrix(data, xUlist, algorithm.version)
  return(lm)
}

```

```{r warning=FALSE, eval=FALSE, echo=FALSE}
res.equal = microbenchmark(compute_likelihood(data.equal, c(U.c.equal, U.e.equal), algorithm.version='Rcpp'), compute_likelihood(data.equal, c(U.c.equal, U.e.equal), algorithm.version='R'), times=100)
```

The time for computing likelihood for data with same se is 

Unit: milliseconds

exper  | min | lq | mean | median | uq | max | neval
------| -----| ---|------|--------|----|-----|------
Rcpp |  866.8975 | 943.1800 | 959.2484 | 957.6582 | 972.0100 | 1227.550 | 100
R | 857.2996 | 945.0444 | 956.5874 | 958.6668 | 971.8977 | 1033.055 | 100

\newline

```{r warning=FALSE, eval=FALSE, echo=FALSE}
res.diff = microbenchmark(compute_likelihood(data.diff, c(U.c.diff, U.e.diff), algorithm.version='Rcpp'), compute_likelihood(data.diff, c(U.c.diff, U.e.diff), algorithm.version='R'), times=100)
```

The time for computing likelihood for data with different se is 

Unit: seconds

exper  | min | lq | mean | median | uq | max | neval
------| -----| ---|------|--------|----|-----|------
Rcpp |  9.8438 | 10.0709 | 10.19134 | 10.1834 | 10.2815 | 10.7816 | 100
R | 9.7953 | 10.0575 | 10.1800 | 10.1376 | 10.2890 | 10.8415 | 100

\newline
 
**Comparisons**:

* Same SE vs Different SE: The computational time for different se data is longer.

* Rcpp vs R: The computational time are similar.

However, from my experience, Rcpp tends to use shorter time in likelihood computation.

# Compare posterior

```{r, echo=FALSE}
m.equal = mash(data.equal, c(U.c.equal, U.e.equal), outputlevel = 1)
m.diff = mash(data.diff, c(U.c.diff, U.e.diff), outputlevel = 1)
```

```{r eval=FALSE, echo=FALSE}
res.post.equal = microbenchmark(mash_compute_posterior_matrices(m.equal, data.equal, algorithm.version = 'Rcpp'), mash_compute_posterior_matrices(m.equal, data.equal, algorithm.version = 'R'), times = 100)
```

The time for computing posterior for data with same se is 

Unit: seconds

exper  | min | lq | mean | median | uq | max | neval
------| -----| ---|------|--------|----|-----|------
Rcpp | 1.0243 | 1.1350 | 1.1753 | 1.1719 | 1.2050 | 1.4510 | 100
R | 1.1636 | 1.2785 | 1.3250 | 1.3143 | 1.3707 | 1.6741 | 100

\newline
 
```{r eval=FALSE, echo=FALSE}
res.post.diff = microbenchmark(mash_compute_posterior_matrices(m.diff, data.diff, algorithm.version = 'Rcpp'), mash_compute_posterior_matrices(m.diff, data.diff, algorithm.version = 'R'), times = 100)
```

The time for computing posterior for data with different se is 

Unit: seconds

exper  | min | lq | mean | median | uq | max | neval
------| -----| ---|------|--------|----|-----|------
Rcpp | 11.2614 | 11.5210 | 11.6741 | 11.6312 | 11.773 | 12.2547 | 100
R | 58.1236 | 58.6919 | 59.3430 | 59.0292 | 59.9362 | 61.2729 | 100

\newline

**Comparisons**:

* Same SE vs Different SE: The computational time for different se data is much longer.

* Rcpp vs R: Rcpp is faster.

# Session information

<!-- Insert the session information into the document -->
```{r session-info}
```
