---
title: "Compare beta and Z"
author: "Yuxin Zou"
date: 2017-11-15
output: html_document
---

<!-- The file analysis/chunks.R contains chunks that define default settings
shared across the workflowr files. -->
```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
knitr::read_chunk('../code/subset.data.R')
knitr::read_chunk("../code/simple_sims_alpha.R")
```

<!-- Update knitr chunk options -->
```{r knitr-opts-chunk, include=FALSE}
```

<!-- Insert the date the file was last updated -->
```{r last-updated, echo=FALSE, results='asis'}
```

<!-- Insert the code version (Git commit SHA1) if Git repository exists and R
 package git2r is installed -->
```{r code-version, echo=FALSE, results='asis'}
```

# Simulate Shat equal data R = 5
```{r}
library(mashr)
set.seed(1)
simdata.equal = simple_sims(500,5,0.5)

# set mash data
TestdataBeta.equal = set_mash_data(simdata.equal$Bhat, simdata.equal$Shat, alpha=0)
TestdataZ.equal = set_mash_data(simdata.equal$Bhat, simdata.equal$Shat, alpha=1)
```

## Create covariance matrices
```{r}
# center
TestdataZ.equal.center = set_mash_data(apply(as.matrix(TestdataZ.equal$Bhat), 2, function(x) x - mean(x)))

# canonical cov
U.c.equal = cov_canonical(TestdataBeta.equal)

# data_driven
m.1by1.Z.equal = mash_1by1(TestdataBeta.equal, alpha=1)
strong.Z.equal = get_significant_results(m.1by1.Z.equal,0.05)
U.pca.Z.equal = cov_pca(TestdataZ.equal.center,5,strong.Z.equal)
```

## EE model
```{r}
U.ed.beta.equal = cov_ed(TestdataBeta.equal, U.pca.Z.equal, strong.Z.equal)
U.m.beta.equal = mash(TestdataBeta.equal, c(U.c.equal,U.ed.beta.equal))

barplot(get_estimated_pi(U.m.beta.equal), las = 2, cex.names = 0.7, main='EE')
```

## EZ model
```{r}
U.ed.Z.equal = cov_ed(TestdataZ.equal, U.pca.Z.equal, strong.Z.equal)
U.m.Z.equal = mash(TestdataZ.equal, c(U.c.equal, U.ed.Z.equal))
barplot(get_estimated_pi(U.m.Z.equal), las = 2, cex.names = 0.7, main='EZ')

```

The estimated weights are similar.
<!--
Check significant samples under transformation A

```{r subset.data}
```

```{r}
A = rbind(c(1,-1,0,0,0))
subset.index = get_significant_results(U.m.beta.equal)
Beta.equal.subset = subset.data(TestdataBeta.equal, subset.index)
Z.equal.subset = subset.data(TestdataZ.equal, subset.index)

# EE
U.m.beta.equal.posterior = mash_compute_posterior_matrices(U.m.beta.equal, Beta.equal.subset, A=A, algorithm.version = 'R')
U.m.beta.equal$result = U.m.beta.equal.posterior

# EZ
U.m.Z.equal.posterior = mash_compute_posterior_matrices(U.m.Z.equal, Z.equal.subset, algorithm.version = 'R', A=A)
U.m.Z.equal$result = U.m.Z.equal.posterior

length(get_significant_results(U.m.beta.equal))
length(get_significant_results(U.m.Z.equal))

```
-->

# Simulate Shat different among conditions, same among samples

```{r}
set.seed(1)
simdata.col.diff = simple_sims(500, 5, rep(c(0.1,0.08,0.15,0.12,0.06), each=2000))
vhat = 0
simdata.col.diff$z = simdata.col.diff$Bhat/simdata.col.diff$Shat

if (vhat == 1) {
  V = cor(simdata.col.diff$z[which(apply(abs(simdata.col.diff$z),1, max) < 2),])
} else {
  V = diag(ncol(simdata.col.diff$z))
}

TestdataBeta.col.diff = set_mash_data(Bhat=simdata.col.diff$Bhat,
                                      Shat=simdata.col.diff$Shat, 
                                      V=as.matrix(V), 
                                      alpha = 0)

TestdataZ.col.diff = set_mash_data(Bhat=simdata.col.diff$Bhat,
                                   Shat=simdata.col.diff$Shat, 
                                   V=as.matrix(V), 
                                   alpha = 1)

```

## Create covariance matrices
```{r}
# center
TestdataZ.col.diff.center = set_mash_data(Bhat = apply(as.matrix(TestdataZ.col.diff$Bhat), 2, function(x) x - mean(x)),
                                          V = as.matrix(V))

# canonical cov
U.c.col.diff = cov_canonical(TestdataBeta.col.diff)

# data_driven
m.1by1.Z.col.diff = mash_1by1(TestdataBeta.col.diff, alpha=1)
strong.Z.col.diff = get_significant_results(m.1by1.Z.col.diff,0.05)
U.pca.Z.col.diff = cov_pca(TestdataZ.col.diff.center,5,strong.Z.col.diff)
```

## EE model
```{r}
U.ed.beta.col.diff = cov_ed(TestdataBeta.col.diff, U.pca.Z.col.diff, strong.Z.col.diff)
U.m.beta.col.diff = mash(TestdataBeta.col.diff, c(U.c.col.diff, U.ed.beta.col.diff))

barplot(get_estimated_pi(U.m.beta.col.diff), las = 2, cex.names = 0.7, main='EE')
```

## EZ model
```{r}
U.ed.Z.col.diff = cov_ed(TestdataZ.col.diff, U.pca.Z.col.diff, strong.Z.col.diff)
U.m.Z.col.diff = mash(TestdataZ.col.diff, c(U.c.col.diff,U.ed.Z.col.diff))
barplot(get_estimated_pi(U.m.Z.col.diff), las = 2, cex.names = 0.7, main='EZ')

```

The estimated weights are different.

```{r}
library('corrplot')
x           <- cov2cor(U.m.Z.col.diff$fitted_g$Ulist[["ED_tPCA"]])
x[x > 1]    <- 1
x[x < -1]   <- -1
corrplot.mixed(x, tl.pos="d",upper='color',cl.lim=c(0.3,1), upper.col=colorRampPalette(rev(c("#D73027","#FC8D59","#FEE090","#FFFFBF",
                               "#E0F3F8","#91BFDB","#4575B4")))(40),
               tl.cex=1.2)
```

```{r}
svd.out = svd(U.m.Z.col.diff$fitted_g$Ulist[["ED_tPCA"]])
v = svd.out$v
options(repr.plot.width=10, repr.plot.height=5)
for (j in 1:1)
  barplot(v[,j]/v[,j][which.max(abs(v[,j]))], cex.names = 0.7,
          las = 2, main = paste0("EigenVector ", j, " for PCA-based covariance matrix"))
```

Check significant samples under transformation A
```{r}
A = rbind(c(1,-1,0,0,0))
subset.data = get_significant_results(U.m.beta.col.diff)
simdata.col.diff.subset = simdata.col.diff
simdata.col.diff.subset$Bhat = simdata.col.diff$Bhat[subset.data,]
simdata.col.diff.subset$Shat = simdata.col.diff$Shat[subset.data,]

TestdataBeta.col.diff.subset = set_mash_data(simdata.col.diff.subset$Bhat, simdata.col.diff.subset$Shat, alpha = 0)
TestdataZ.col.diff.subset = set_mash_data(simdata.col.diff.subset$Bhat, simdata.col.diff.subset$Shat, alpha = 1)

# EE
U.m.beta.col.diff.posterior = mash_compute_posterior_matrices(U.m.beta.col.diff, TestdataBeta.col.diff.subset, A=A, algorithm.version = 'R')
U.m.beta.col.diff$result = U.m.beta.col.diff.posterior

# EZ
U.m.Z.col.diff.posterior = mash_compute_posterior_matrices(U.m.Z.col.diff, TestdataZ.col.diff.subset, A=A, algorithm.version = 'R')
U.m.Z.col.diff$result = U.m.Z.col.diff.posterior

length(get_significant_results(U.m.beta.col.diff))
length(get_significant_results(U.m.Z.col.diff))
```

Comparing loglikelihood
```{r}
get_loglik(U.m.beta.col.diff)
get_loglik(U.m.Z.col.diff)
```
EE model has higher likelihood, since the data is simulated under EE.

# Simulate Shat different among samples, same among conditions

```{r}
set.seed(1)
simdata.samp.diff = simple_sims(500, 5, rep(c(0.5,0.4,5,1,1), 400))
vhat = 0
simdata.samp.diff$z = simdata.samp.diff$Bhat/simdata.samp.diff$Shat

if (vhat == 1) {
  V = cor(simdata.samp.diff$z[which(apply(abs(simdata.samp.diff$z),1, max) < 2),])
} else {
  V = diag(ncol(simdata.samp.diff$z))
}

TestdataBeta.samp.diff = set_mash_data(Bhat=simdata.samp.diff$Bhat,
                                      Shat=simdata.samp.diff$Shat, 
                                      V=as.matrix(V), 
                                      alpha = 0)

TestdataZ.samp.diff = set_mash_data(Bhat=simdata.samp.diff$Bhat,
                                   Shat=simdata.samp.diff$Shat, 
                                   V=as.matrix(V), 
                                   alpha = 1)
```

## Create covariance matrices

```{r}
# center
TestdataZ.samp.diff.center = set_mash_data(Bhat = apply(as.matrix(TestdataZ.samp.diff$Bhat), 2, function(x) x - mean(x)))

# canonical cov
U.c.samp.diff = cov_canonical(TestdataBeta.samp.diff)

# data_driven from Z
m.1by1.Z.samp.diff = mash_1by1(TestdataBeta.samp.diff, alpha=1)
strong.Z.samp.diff = get_significant_results(m.1by1.Z.samp.diff,0.05)
U.pca.Z.samp.diff = cov_pca(TestdataZ.samp.diff.center,5,strong.Z.samp.diff)

```

## EE model
```{r}
U.ed.beta.samp.diff = cov_ed(TestdataBeta.samp.diff, U.pca.Z.samp.diff, strong.Z.samp.diff)
U.m.beta.samp.diff = mash(TestdataBeta.samp.diff, 
                          c(U.c.samp.diff, U.ed.beta.samp.diff))

barplot(get_estimated_pi(U.m.beta.samp.diff), las = 2, cex.names = 0.7, main='EE')
```

## EZ model
```{r}
U.ed.Z.samp.diff = cov_ed(TestdataZ.samp.diff, U.pca.Z.samp.diff, strong.Z.samp.diff)
U.m.Z.samp.diff = mash(TestdataZ.samp.diff, c(U.c.samp.diff, U.ed.Z.samp.diff))
barplot(get_estimated_pi(U.m.Z.samp.diff), las = 2, cex.names = 0.7, main='EZ')
```

**The estiamted weights are different if the Shat is not constant.**

Comparing loglikelihood
```{r}
get_loglik(U.m.beta.samp.diff)
get_loglik(U.m.Z.samp.diff)
```
Again, EE model has higher likelihood, since the data is simulated under EE.

Check significant samples under transformation A
```{r}
A = rbind(c(1,-1,0,0,0))
subset.data = get_significant_results(U.m.beta.samp.diff)
simdata.samp.diff.subset = simdata.samp.diff
simdata.samp.diff.subset$Bhat = simdata.samp.diff$Bhat[subset.data,]
simdata.samp.diff.subset$Shat = simdata.samp.diff$Shat[subset.data,]

TestdataBeta.samp.diff.subset = set_mash_data(simdata.samp.diff.subset$Bhat, simdata.samp.diff.subset$Shat, alpha = 0)
TestdataZ.samp.diff.subset = set_mash_data(simdata.samp.diff.subset$Bhat, simdata.samp.diff.subset$Shat, alpha = 1)

# EE
U.m.beta.samp.diff.posterior = mash_compute_posterior_matrices(U.m.beta.samp.diff, TestdataBeta.samp.diff, A=A, algorithm.version = 'R')
U.m.beta.samp.diff$result = U.m.beta.samp.diff.posterior

# EZ
U.m.Z.samp.diff.posterior = mash_compute_posterior_matrices(U.m.Z.samp.diff, TestdataZ.samp.diff, A=A, algorithm.version = 'R')
U.m.Z.samp.diff$result = U.m.Z.samp.diff.posterior

length(get_significant_results(U.m.beta.samp.diff))
length(get_significant_results(U.m.Z.samp.diff))
```

# Simulation based on $\alpha$

Simulation function
```{r simple_sims_alpha}
```

Set mash data
```{r}
set.seed(1)
simdata.diff = simple_sims_alpha(500, 5, c(0.2,0.3,0.4,0.2,0.3), alpha = 0.8)
vhat = 0
simdata.diff$z = simdata.diff$Bhat/simdata.diff$Shat

if (vhat == 1) {
  V = cor(simdata.diff$z[which(apply(abs(simdata.diff$z),1, max) < 2),])
} else {
  V = diag(ncol(simdata.diff$z))
}

TestdataBeta.diff = set_mash_data(Bhat=simdata.diff$Bhat,
                                      Shat=simdata.diff$Shat, 
                                      V=as.matrix(V), 
                                      alpha = 0)

TestdataZ.diff = set_mash_data(Bhat=simdata.diff$Bhat,
                                   Shat=simdata.diff$Shat, 
                                   V=as.matrix(V), 
                                   alpha = 1)

```

Create covariance matrices
```{r}
# center
TestdataZ.diff.center = set_mash_data(Bhat=apply(as.matrix(TestdataZ.diff$Bhat), 2, function(x) x - mean(x)))

# canonical cov
U.c.diff = cov_canonical(TestdataBeta.diff)

# data_driven from Z
m.1by1.Z.diff = mash_1by1(TestdataBeta.diff, alpha=1)
strong.Z.diff = get_significant_results(m.1by1.Z.diff,0.05)
U.pca.Z.diff = cov_pca(TestdataZ.diff.center,5,strong.Z.diff)

```

## EE model
```{r}
U.ed.beta.diff = cov_ed(TestdataBeta.diff, U.pca.Z.diff, strong.Z.diff)
U.m.beta.diff = mash(TestdataBeta.diff, c(U.c.diff, U.ed.beta.diff))

barplot(get_estimated_pi(U.m.beta.diff), las = 2, cex.names = 0.7, main='EE')
```

## EZ model
```{r}
U.ed.Z.diff = cov_ed(TestdataZ.diff, U.pca.Z.diff, strong.Z.diff)
U.m.Z.diff = mash(TestdataZ.diff, c(U.c.diff, U.ed.Z.diff))
barplot(get_estimated_pi(U.m.Z.diff), las = 2, cex.names = 0.7, main='EZ')

```

Compare loglikelihod
```{r}
get_loglik(U.m.beta.diff)
get_loglik(U.m.Z.diff)
```

The data is simulated using $\alpha = 0.8$, which is near 1. The EZ model has larger log likelihood.

If the Shat are different for different condition or samples, the estimated weights are different using EE, EZ models. Using the EZ model, the covariance structures we found are about the standardized effects. Using the EE model, the covariance structure are about the raw effects.

The estimated weights are for covariance matrices instead of correlation matrices. If EZ model puts large weight on equal effect cov ($11’$), it means that the standardized effects $S_{j}^{-1} \beta_{j}$ are strongly correlated among conditions. But this means the raw effect $\beta_{j}$ has cov $S_{j}11’S_{j}$, which does not proportional to $11’$ (if diagonal of $S_{j}$ are not equal). Therefore, in the EE model, it will put large weight on cov $S_{j}11’S_{j}$, instead of $11’$. The covariance structure we found are different, but the correlation structure could be same.

# Session information

<!-- Insert the session information into the document -->
```{r session-info}
```
