---
title: "Comparing with mean (without signal)"
author: "Yuxin Zou"
date: 2018-01-10
output: html_document
---
```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
```

<!-- Update knitr chunk options -->
```{r knitr-opts-chunk, include=FALSE}
```

<!-- Insert the date the file was last updated -->
```{r last-updated, echo=FALSE, results='asis'}
```

<!-- Insert the R version (Git commit SHA1) if Git repository exists and R
 package git2r is installed -->
```{r R-version, echo=FALSE, results='asis'}
```

```{r, echo=FALSE}
# TEMPORARY.
knitr::opts_chunk$set(eval = TRUE)
```

```{r, echo=FALSE}
library(mashr)
```

# Simulation without signal

$$c_{j} = \mu_{j} 1$$
$$\hat{c}_{j} \sim N_{R}(c_{j}, \frac{1}{2}I)$$
Let L be the contrast matrix, which comparing each condition with the mean. 
$$L = \left(\begin{array}{c c c c}
\frac{R-1}{R} & -\frac{1}{R} & \cdots & -\frac{1}{R} \\
-\frac{1}{R} & \frac{R-1}{R} & \cdots & -\frac{1}{R} \\
\vdots & \ddots & \ddots & \vdots \\
-\frac{1}{R} & \cdots & \frac{R-1}{R} & -\frac{1}{R}
\end{array} \right)_{R-1 \times R}$$
There are only R-1 rows, intead of R. Since $c_{j,R}-\bar{c_{j}} = -\sum_{r=1}^{R-1} (c_{j,r}-\bar{c_{j}})$.

Therefore, $$\hat{\delta}_{j} = L\hat{c}_{j} \sim N_{R-1}(0, \frac{1}{2}LL')$$

We first generate the data:
```{r}
set.seed(1)
data = sim.contrast1(nsamp = 10000, ncond = 8)
```

# Mash contrast model

Set up the contrast matrix and the mash contrast data object
```{r}
L = rbind(c(7/8,-1/8,-1/8,-1/8,-1/8,-1/8,-1/8,-1/8),
          c(-1/8,7/8,-1/8,-1/8,-1/8,-1/8,-1/8,-1/8),
          c(-1/8,-1/8,7/8,-1/8,-1/8,-1/8,-1/8,-1/8),
          c(-1/8,-1/8,-1/8,7/8,-1/8,-1/8,-1/8,-1/8),
          c(-1/8,-1/8,-1/8,-1/8,7/8,-1/8,-1/8,-1/8),
          c(-1/8,-1/8,-1/8,-1/8,-1/8,7/8,-1/8,-1/8),
          c(-1/8,-1/8,-1/8,-1/8,-1/8,-1/8,7/8,-1/8))
row.names(L) = seq(1,7)
mash_data = mash_set_data(Bhat=data$Chat, Shat=data$Shat)
mash_data_L = mash_set_data_contrast(mash_data, L)
```

Set up the covariance matrices:

```{r}
U.c = cov_canonical(mash_data_L)
```

Fit `mashcontrast` model
```{r}
mashcontrast.model = mash(mash_data_L, U.c, algorithm.version = 'R')
```

```{r}
length(get_significant_results(mashcontrast.model))
```
There is no discovery, which is as we expected. The true deviations from mean are zero for all samples.

```{r}
barplot(get_estimated_pi(mashcontrast.model),las = 2, cex.names = 0.7)
```

# Subtract mean directly

If we subtract the mean from the data directly, ignoring the correlation structure.
$$Var(\hat{c}_{j,r}-\bar{\hat{c}_{j}}) = \frac{1}{2} - \frac{1}{2R}$$
```{r}
Indep.data = mash_set_data(Bhat = (data$Chat - apply(data$Chat,1, mean))[,1:7],
                           Shat = matrix(sqrt(0.5-1/(8*2)), nrow(data$Chat), ncol(data$Chat)-1))
U.c = cov_canonical(mash_data_L)
Indep.model = mash(Indep.data, U.c, algorithm.version = 'R')
```
```{r}
length(get_significant_results(Indep.model))
```
There are no false positives.

```{r}
barplot(get_estimated_pi(Indep.model),las = 2)
```

When there are no signal, subtracting mean directly from the data performs as good as the `mashcommonbaseline` model.

# Session information

<!-- Insert the session information into the document -->
```{r session-info}
```
