---
title: "Flash"
author: "Yuxin Zou"
date: 2017-12-08
output: html_document
---

```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
```

<!-- Update knitr chunk options -->
```{r knitr-opts-chunk, include=FALSE}
```

<!-- Insert the date the file was last updated -->
```{r last-updated, echo=FALSE, results='asis'}
```

<!-- Insert the code version (Git commit SHA1) if Git repository exists and R
 package git2r is installed -->
```{r code-version, echo=FALSE, results='asis'}
```

# Case 1: 2 dim

*  Generate data
```{r}
library(MASS)
library(flashr2)
Means <- rep(0,2)
set.seed(1)
x1 <- mvrnorm(n = 1000, Means, diag(c(1,0)))
x2 <- mvrnorm(n = 1000, Means, diag(c(0,1)))
Sigma = cbind(c(1,1), c(1,1))
x3 = mvrnorm(n = 1000, Means, Sigma)
x = rbind(x1,x2, x3)
# plus error
x = x + matrix(rnorm(6000, 0, 0.05), nrow=3000, ncol=2)
plot(x)
```

*  Flash

```{r warning=FALSE}
data = flash_set_data(x)
fg = flash_add_greedy(data,10, var_type = 'constant')
fb = flash_backfit(data,fg)
flash_get_F(data,fb)
```

The warnings are muted here. 

```{r}
par(mfrow=c(1,2))
barplot(flash_get_f(fb,1), main='loading 1')
barplot(flash_get_f(fb,2), main='loading 2')
par(mfrow=c(1,1))
```

The algorithm converges to a local optimum.

If we initialize the flash with 3 fixed factors
```{r}
lfixf = flash_add_fixed_f(data,FF=cbind(c(1,1),c(1,0),c(0,1)))
```

The loadings found here are all 0.

Fit the flash model to data

```{r}
fixfb = flash_backfit(data,lfixf)
flash_get_F(data,fixfb)
```

The value of objective function becomes worse. 

# Case 2: 5 conditions

*  Generate data

There are 5 conditions with 8 factors: 10000, 01000, 00100, 00010, 00001 and also 11111 and 11000 and 00111.

```{r}
sim = function(nsamp=100, err_sd=1){
  ncond=5
  B.0 = matrix(0, nrow = nsamp, ncol = ncond)
  B.1 = B.0; B.2 = B.0; B.3 = B.0; B.4 = B.0; B.5 = B.0
  b = rnorm(nsamp)
  B.1[,1] = b; 
  b = rnorm(nsamp)
  B.2[,2] = b; 
  b = rnorm(nsamp)
  B.3[,3] = b; 
  b = rnorm(nsamp)
  B.4[,4] = b; 
  b = rnorm(nsamp)
  B.5[,5] = b; 
  
  b = rnorm(nsamp)
  B.all = matrix(rep(b, 5), nrow = nsamp, ncol = ncond)
  
  b1 = rnorm(nsamp)
  B.11 = matrix(cbind(b1, b1, 0, 0, 0), nrow = nsamp, ncol = ncond)
  
  b2 = rnorm(nsamp)
  B.111 = matrix(cbind(0, 0, b2, b2, b2), nrow = nsamp, ncol = ncond)
  B = rbind(B.1, B.2, B.3, B.4, B.5, B.all, B.11, B.111)
  
  Shat = matrix(err_sd, nrow = nrow(B), ncol = ncol(B))
  E = matrix(rnorm(length(Shat), mean = 0, sd = Shat), nrow = nrow(B), 
        ncol = ncol(B))
  Bhat = B + E
  
  row_ids = paste0("effect_", 1:nrow(B))
  col_ids = paste0("condition_", 1:ncol(B))
  rownames(B) = row_ids
  colnames(B) = col_ids
  rownames(Bhat) = row_ids
  colnames(Bhat) = col_ids
  rownames(Shat) = row_ids
  colnames(Shat) = col_ids
  return(list(B = B, Bhat = Bhat, Shat = Shat))
}
```

```{r}
set.seed(1)
x = sim(nsamp=5000, err_sd = 0.05)
```

## Flash

Only 5 factors with 'by_column' type variance.

```{r warning=FALSE}
data = flash_set_data(x$Bhat)
fg = flash_add_greedy(data, Kmax=10, var_type='constant')
fb = flash_backfit(data,fg)
flash_get_F(data,fb)
```

```{r}
layout(matrix(c(1,2,3,4,5,6), 3, 2, byrow = TRUE))
barplot(flash_get_f(fb, 1), main='loading 1')
barplot(flash_get_f(fb, 2), main='loading 2')
barplot(flash_get_f(fb, 3), main='loading 3')
barplot(flash_get_f(fb, 4), main='loading 4')
barplot(flash_get_f(fb, 5), main='loading 5')
barplot(flash_get_f(fb, 6), main='loading 6')
```

If we initialize the flash with 8 fixed factors
```{r}
lfixf = flash_add_fixed_f(data,FF=cbind(c(1,1,0,0,0),c(0,0,1,1,1),c(1,1,1,1,1),
                                        c(1,0,0,0,0),c(0,1,0,0,0),c(0,0,1,0,0),
                                        c(0,0,0,1,0),c(0,0,0,0,1)))
fixfb = flash_backfit(data,lfixf)
flash_get_F(data,fixfb)
```

The value of objective function becomes higher.

# Session information

<!-- Insert the session information into the document -->
```{r session-info}
```
