---
title: "MASH-Flash 2 factor"
author: "Yuxin Zou"
date: 2018-01-23
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
```

<!-- Update knitr chunk options -->
```{r knitr-opts-chunk, include=FALSE}
```

<!-- Insert the date the file was last updated -->
```{r last-updated, echo=FALSE, results='asis'}
```

<!-- Insert the R version (Git commit SHA1) if Git repository exists and R
 package git2r is installed -->
```{r R-version, echo=FALSE, results='asis'}
```

```{r, echo=FALSE}
# TEMPORARY.
knitr::opts_chunk$set(eval = TRUE)
```


```{r echo=FALSE}
library(flashr)
library(mashr)
library(corrplot)
source('../code/sim_flash.R')
```

# Generate data

The data is generated that some of them depend on two factors.

```{r}
set.seed(50)
data = sim.flash(nsamp=1000, err_sd = 0.05)
```

* `flashr` Factorization

```{r eval=FALSE}
z = data$Bhat/data$Shat
# center
Z.center = apply(z, 2, function(x) x - mean(x))

fdata = flash_set_data(Z.center)
fg = flash_add_greedy(fdata,10, seed=2000)
fb = flash_backfit(fdata,fg)

saveRDS(fb, '../output/FLash_2_fb.rds')
```

The factor structures:

```{r echo=FALSE}
fb = readRDS('../output/FLash_2_fb.rds')
layout(matrix(c(1,2,3), 1, 3, byrow = TRUE))
barplot(flash_get_f(fb,1), main = 'loading 1')
barplot(flash_get_f(fb,2), main = 'loading 2')
barplot(flash_get_f(fb,3), main = 'loading 3')
```

# Apply `mash` without factor rank 1 covariance

```{r echo=FALSE}
mash_data = mash_set_data(Bhat = data$Bhat, Shat = data$Shat)
U.c = cov_canonical(mash_data)
U.flash = c(list("tFlash" = t(flash_get_lf(fb)) %*% flash_get_lf(fb) / nrow(mash_data$Bhat)))

U.ed = cov_ed(mash_data, U.flash)
mash_model = mash(mash_data, c(U.c,U.ed), algorithm.version = 'R', verbose = FALSE)
barplot(get_estimated_pi(mash_model), las=2, cex.names = 0.7)
```

The `mash` model puts the majority weights on `tFlash`. There are `r length(get_significant_results(mash_model))` siginificant findings. The log likelihood is `r get_loglik(mash_model)`.

# Apply `mash` with factor rank 1 covariance, without rank 2 matrices 

```{r echo=FALSE}
U.flash.1 = c(mashr::cov_from_factors(t(as.matrix(flash_get_f(fb,1:3))), "Flash"),
            list("tFlash" = t(flash_get_lf(fb)) %*% flash_get_lf(fb) / nrow(mash_data$Bhat)))

U.ed.1 = cov_ed(mash_data, U.flash.1)
mash_model.1 = mash(mash_data, c(U.c,U.ed.1), algorithm.version = 'R', verbose = FALSE)
barplot(get_estimated_pi(mash_model.1), las=2, cex.names = 0.7)
```

Again, the `mash` model put a large postion of weights on `tFlash`. There are `r length(get_significant_results(mash_model.1))` siginificant findings. The log likelihood is `r get_loglik(mash_model.1)`.

The `mash` model with rank 1 factor covariances has higher likelihood value.

# Apply `mash` with factor rank 2 covariance

## Method 1: Naive way

```{r}
flash_get_pve(fb)
```

Add $F_{s}L_{s}'L_{s}F_{s}'$, s is $\{1,2\}, \{1,3\}, \{2,3\}$

```{r}
# every two factor combination
Flash12 = flash_get_l(fb, 1:2) %*% t(flash_get_f(fb,1:2))
Flash12 = t(Flash12) %*% Flash12
Flash13 = flash_get_l(fb, c(1,3)) %*% t(flash_get_f(fb,c(1,3)))
Flash13 = t(Flash13) %*% Flash13
Flash23 = flash_get_l(fb, 2:3) %*% t(flash_get_f(fb,2:3))
Flash23 = t(Flash23) %*% Flash23

U.flash.2.1 = c(mashr::cov_from_factors(t(as.matrix(flash_get_f(fb,1:3))), "Flash"),
            list("Flash12" = Flash12, "Flash13" = Flash13, "Flash23" = Flash23, "tFlash" = t(flash_get_lf(fb)) %*% flash_get_lf(fb) / nrow(mash_data$Bhat)))

U.ed.2.1 = cov_ed(mash_data, U.flash.2.1)
mash_model.2.1 = mash(mash_data, c(U.c,U.ed.2.1), algorithm.version = 'R', verbose = FALSE)
barplot(get_estimated_pi(mash_model.2.1), las=2, cex.names = 0.7)
```
The `mash` model identifies the covariacne structure correctly. There are `r length(get_significant_results(mash_model.2.1))` siginificant findings. The log likelihood is `r get_loglik(mash_model.2.1)`.

With the correct covariance struture, the `mash` model has a much higher likelihood value. Adding rank 2 factor covariance improves the fitting.

This method is unrealistic if the number of factors is large. 

## Method 2: Clustering loadings

See [Flash_loading_2](Flash_loading_2.html)

# Session information

<!-- Insert the session information into the document -->
```{r session-info}
```

