---
title: "Immune Flash Covariance individual reduce"
author: "Yuxin Zou"
date: 2017-12-29
output: html_document
---
```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
```

<!-- Update knitr chunk options -->
```{r knitr-opts-chunk, include=FALSE}
```

<!-- Insert the date the file was last updated -->
```{r last-updated, echo=FALSE, results='asis'}
```

<!-- Insert the code version (Git commit SHA1) if Git repository exists and R
 package git2r is installed -->
```{r code-version, echo=FALSE, results='asis'}
```

```{r, echo=FALSE}
# TEMPORARY.
knitr::opts_chunk$set(eval = TRUE)
```

# Set up the data
```{r}
# Load required packages
library(mashr); library(ExtremeDeconvolution); library(flashr2); library(mclust)
```
```{r}
# read data
data = readRDS('../data/ImmuneQTLSummary.4MASH.rds')
data$max$se = data$max$beta/data$max$z
data$null$se = data$null$beta / data$null$z
# set parameters
vhat = 1
```
We estimate the covariance using column-centered Z scores
```{r}
D.center = apply(as.matrix(data$max$z), 2, function(x) x - mean(x))
mash_data_center = mashr::set_mash_data(Bhat = as.matrix(D.center))
```

# Generate covariance matrices for each row

From [Flash](Immune_Flash.html), we have $$\tilde{Z} = LF' + E$$
where F is $7 \times 5$, L is $n \times 5$, E is $n\times7$.

$$F = \left( \begin{array}{c c c c}
f_{1} & f_{2} & \cdots & f_{5}
\end{array}\right)_{p\times 5}$$
For each gene i, $$z_{i} = \sum_{k=1}^{5}l_{ik} f_{k}$$. The covariance matrix for gene i is $$U_{i} = z_{i}z_{i}'$$ which could capture the patterns in the ith sample.

```{r}
FlashResult = readRDS('~/Documents/GitHub/mash-application-immune/output/Immune.flash2.center.greedy.K10.rds')
n = nrow(FlashResult$L_flash)
U = list()
Z = matrix(0, nrow=n, ncol=7)
for(i in 1:n){
  zi = apply(t(FlashResult$L_flash[i,] * t(FlashResult$F_flash)), 1, sum)
  Z[i,] = zi
  U[[i]] = zi %*% t(zi) 
}
```

The covariance matrices for two genes will be similar if they have similar $z_{i}$ vectors.

So we try to cluster $z_{i}$ vectors.
```{r}
mod <- Mclust(Z)
summary(mod$BIC)
summary(mod, parameters = TRUE)
```
There is only one cluster identified here. The estimated model is $$z_{i} \sim N_{7}(\hat{\mu}, \hat{\Sigma})$$

```{r}
saveRDS(list(mod$parameters$variance$Sigma), '../output/Immune.flash.ind.reduce.cov.rds')
```

We can use this estiamted $\hat{\Sigma}$ to estiamte the covariance matrix for all genes.

# Session information

<!-- Insert the session information into the document -->
```{r session-info}
```
