---
title: "Immune Data MASH Model Covariance (EE)"
author: "Yuxin Zou"
date: 2017-11-16
output: html_document
---
```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
```

<!-- Update knitr chunk options -->
```{r knitr-opts-chunk, include=FALSE}
```

<!-- Insert the date the file was last updated -->
```{r last-updated, echo=FALSE, results='asis'}
```

<!-- Insert the code version (Git commit SHA1) if Git repository exists and R
 package git2r is installed -->
```{r code-version, echo=FALSE, results='asis'}
```

```{r, echo=FALSE}
# TEMPORARY.
knitr::opts_chunk$set(eval = TRUE)
```

# Set up the data
```{r}
# Load required packages
library(mashr); library(ExtremeDeconvolution); library(flashr2)
```
```{r}
# read data
data = readRDS('../data/ImmuneQTLSummary.4MASH.rds')
data$max$se = data$max$beta/data$max$z
data$null$se = data$null$beta / data$null$z

# set parameters
K = 10
P = 5
```

We estimate the covariance using column-centered Z scores
```{r}
D.center = apply(as.matrix(data$max$z), 2, function(x) x - mean(x))
mash_data_center = mashr::set_mash_data(Bhat = as.matrix(D.center))
```

# Generate covariance matrices

Here we create 3 type of data-driven covariance matrices:

* Flash (rank 5, previously computed): [Flash](Immune_Flash.html)
  $$ \tilde{Z}_{n\times 7} = LF' + E $$
  $$ U = \frac{1}{n} (LF')'(LF') $$
    + plus single rank Flashs for each factor
    The 5 matrices $F_{q}L_{q}' L_{q} F_{q}'$
    
* PCA (rank 5, to be computed)
    + plus single rank PCAs
    
* Optionally
    + Empirical covariance
    
and apply `Extreme Deconvolution` to refine these matrices. We observed that Extreme Deconvolution perserves rank.

Additionally we include 2 other types of covariance matrices:

* canonical configurations (aka `bmalite`)

* simple heterogeneity models

## Generate and refine multi-rank data-driven covariance matrices

```{r}
FlashResult = readRDS('../output/Immune.flash2.center.greedy.K10.rds')
Flash_res = flash_get_lf(FlashResult$f)

U.flash = c(mashr::cov_from_factors(t(as.matrix(FlashResult$F_flash[,1:5])), "Flash"), 
            list("tFlash" = t(Flash_res) %*% Flash_res / nrow(data$max$z)))

# PCA matrices
U.pca = cov_pca(mash_data_center, P)

# Emperical data matrices
# Denoised data-driven matrices
U.dd = c(U.flash, U.pca, list("XX" = t(D.center) %*% D.center / nrow(data$max$z)))

mash_data = mashr::set_mash_data(Bhat = as.matrix(data$max$beta), 
                                 Shat = as.matrix(data$max$se), alpha=0)

U.ed = cov_ed(mash_data, U.dd)
```

## Generate canonical covariance matrices

```{r}
# Canonical
U.can = cov_canonical(mash_data) 

# save Covariance matrix
saveRDS(list(Ulist = c(U.ed, U.can), DD_raw = U.dd), 
        paste0('../output/ImmuneEE.U.center.xtx.K',K,'.P',P,'.rds'))

```

# Session information

<!-- Insert the session information into the document -->
```{r session-info}
```
