---
title: "Immune Data Mash Analysis EZ V1 reQTLs Results"
author: "Yuxin Zou"
date: 2017-11-20
output: html_document
---
```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
knitr::read_chunk('../code/subset.data.R')
```

<!-- Update knitr chunk options -->
```{r knitr-opts-chunk, include=FALSE}
```

<!-- Insert the date the file was last updated -->
```{r last-updated, echo=FALSE, results='asis'}
```

<!-- Insert the code version (Git commit SHA1) if Git repository exists and R
 package git2r is installed -->
```{r code-version, echo=FALSE, results='asis'}
```

# Set up data
```{r}
library(lattice)
library(ggplot2)
library(colorRamps)
library(mashr)
library(corrplot)
data = readRDS('../data/ImmuneQTLSummary.4MASH.rds')
data$max$se = data$max$beta/data$max$z
data$null$se = data$null$beta / data$null$z

K = 10
P = 5
vhat = 1
```

```{r}
if (vhat == 1) {
  V = cor(data$null$z[which(apply(abs(data$null$z),1, max) < 2),])
} else {
  V = diag(ncol(data$null$z))
}

# standardized effect
mash_data = mashr::set_mash_data(Bhat = as.matrix(data$max$beta)/as.matrix(data$max$se), 
                                 Shat = 1, 
                                 V = as.matrix(V), 
                                 alpha = 1)
```

# MASH results

```{r}
# EZ
resEZ = readRDS('../output/ImmuneEZ.V1.center.mash_model.K10.P5.rds')
resEZ$result = readRDS('../output/ImmuneEZ.V1.center.mash_posterior.K10.P5.rds')
```

Here is a plot of weights learned.

```{r}
options(repr.plot.width=12, repr.plot.height=4)
barplot(get_estimated_pi(resEZ), las = 2, cex.names = 0.7)
```

* Original estimates
```{r echo=FALSE}
# raw effect
stronggene = data.frame(data$max$beta[8553,])
colnames(stronggene) = 'EffectSize'
stronggene$Group = row.names(stronggene)
stronggene$se = data$max$se[8553,]
ggplot(stronggene, aes(y = EffectSize, x = Group, color=Group)) + 
  geom_point() + geom_hline(yintercept = 0) + 
  geom_errorbar(aes(ymin=EffectSize-1.96*se, ymax=EffectSize+1.96*se), width=0.4) + 
  theme_bw(base_size=12) + coord_flip() + ggtitle('ILMN_1753575_rs200826215 ')
```

* `MASH` estimates

```{r echo=FALSE}
# Improved
stronggenePost = data.frame(resEZ$result$PosteriorMean[8553,])
colnames(stronggenePost) = 'EffectSize'
stronggenePost$Group = row.names(stronggenePost)
stronggenePost$se = resEZ$result$PosteriorSD[8553,]
ggplot(stronggenePost, aes(y = EffectSize, x = Group, color=Group)) + 
  geom_point() + geom_hline(yintercept = 0) + 
  geom_errorbar(aes(ymin=EffectSize-1.96*se, ymax=EffectSize+1.96*se), width=0.4) + 
  theme_bw(base_size=12) + coord_flip() + ggtitle('ILMN_1753575_rs200826215 ')
```


## reQTLs
The reQTL is defined as different **standardized** effects. Find genes having $\beta_{Trt}/s$ significantly different from $\beta_{Ctrl}/s$, among the top eQTLs.

```{r subset.data}
```

### LPS 6h
```{r}
# Define A
eQTL.index.lps6h = get_significant_results(resEZ, conditions = 2)
A.lps6h = rbind(c(1,-1,0,0,0,0,0))
row.names(A.lps6h) = c('Ctrl-lps6h')
```

```{r}
resEZ.lps6h = resEZ
eQTL.lps6h = subset.data(mash_data, eQTL.index.lps6h)
resEZ.lps6h$result = mash_compute_posterior_matrices(resEZ, eQTL.lps6h, A=A.lps6h, algorithm.version = 'R')
saveRDS(resEZ.lps6h, 
        paste0('../output/ImmuneEZ.V',vhat,'.center.resEZ.reQTL.lps6h.K',K,'.P',P,'.rds'))

```

```{r}
resEZ.lps6h = readRDS(paste0('../output/ImmuneEZ.V',vhat,'.center.resEZ.reQTL.lps6h.K',K,'.P',P,'.rds'))
length(get_significant_results(resEZ.lps6h))
```

Using `MASH`, we found `r round(length(get_significant_results(resEZ.lps6h))/length(eQTL.index.lps6h) * 100,2)`% [17%] of lps 6h eQTLs are reQTLs.

### LPS 90
```{r, echo=FALSE}
eQTL.index.lps90 = get_significant_results(resEZ, conditions = 3)
A.lps90 = rbind(c(1,0,-1,0,0,0,0))
row.names(A.lps90) = c('Ctrl-lps90')
```

```{r, echo=FALSE}
resEZ.lps90 = resEZ
eQTL.lps90 = subset.data(mash_data, eQTL.index.lps90)
resEZ.lps90$result = mash_compute_posterior_matrices(resEZ, eQTL.lps90, A=A.lps90, algorithm.version = 'R')
saveRDS(resEZ.lps90, 
        paste0('../output/ImmuneEZ.V',vhat,'.center.resEZ.reQTL.lps90.K',K,'.P',P,'.rds'))

```

```{r}
resEZ.lps90 = readRDS(paste0('../output/ImmuneEZ.V',vhat,'.center.resEZ.reQTL.lps90.K',K,'.P',P,'.rds'))
length(get_significant_results(resEZ.lps90))
```

We found `r round(length(get_significant_results(resEZ.lps90))/length(eQTL.index.lps90) * 100,2)`% [15%] of lps 90 eQTLs are reQTLs.

### MDP 6h
```{r, echo=FALSE}
eQTL.index.mdp6h = get_significant_results(resEZ, conditions = 4)
A.mdp6h = rbind(c(1,0,0,-1,0,0,0))
row.names(A.mdp6h) = c('Ctrl-mdp6h')
```

```{r, echo=FALSE}
resEZ.mdp6h = resEZ
eQTL.mdp6h = subset.data(mash_data, eQTL.index.mdp6h)
resEZ.mdp6h$result = mash_compute_posterior_matrices(resEZ, eQTL.mdp6h, A=A.mdp6h, algorithm.version = 'R')
saveRDS(resEZ.mdp6h, 
        paste0('../output/ImmuneEZ.V',vhat,'.center.resEZ.reQTL.mdp6h.K',K,'.P',P,'.rds'))

```

```{r}
resEZ.mdp6h = readRDS(paste0('../output/ImmuneEZ.V',vhat,'.center.resEZ.reQTL.mdp6h.K',K,'.P',P,'.rds'))
length(get_significant_results(resEZ.mdp6h))
```

We found `r round(length(get_significant_results(resEZ.mdp6h))/length(eQTL.index.mdp6h) * 100,2)`% [9%] of mdp 6h eQTLs are reQTLs.

### MDP 90
```{r, echo=FALSE}
eQTL.index.mdp90 = get_significant_results(resEZ, conditions = 5)
A.mdp90 = rbind(c(1,0,0,0,-1,0,0))
row.names(A.mdp90) = c('Ctrl-mdp90')
```

```{r, echo=FALSE}
resEZ.mdp90 = resEZ
eQTL.mdp90 = subset.data(mash_data, eQTL.index.mdp90)
resEZ.mdp90$result = mash_compute_posterior_matrices(resEZ, eQTL.mdp90, A=A.mdp90, algorithm.version = 'R')
saveRDS(resEZ.mdp90, 
        paste0('../output/ImmuneEZ.V',vhat,'center.resEZ.reQTL.mdp90.K',K,'.P',P,'.rds'))

```

```{r}
resEZ.mdp90 = readRDS(paste0('../output/ImmuneEZ.V',vhat,'center.resEZ.reQTL.mdp90.K',K,'.P',P,'.rds'))
length(get_significant_results(resEZ.mdp90))
```

We found `r round(length(get_significant_results(resEZ.mdp90))/length(eQTL.index.mdp90) * 100,2)`% [9%] of mdp 90 eQTLs are reQTLs.

### RNA 6h
```{r, echo=FALSE}
eQTL.index.rna6h = get_significant_results(resEZ, conditions = 6)
A.rna6h = rbind(c(1,0,0,0,0,-1,0))
row.names(A.rna6h) = c('Ctrl-rna6h')
```

```{r, echo=FALSE}
resEZ.rna6h = resEZ
eQTL.rna6h = subset.data(mash_data, eQTL.index.rna6h)
resEZ.rna6h$result = mash_compute_posterior_matrices(resEZ, eQTL.rna6h, A=A.rna6h, algorithm.version = 'R')
saveRDS(resEZ.rna6h, 
        paste0('../output/ImmuneEZ.V',vhat,'.center.resEZ.reQTL.rna6h.K',K,'.P',P,'.rds'))

```

```{r}
resEZ.rna6h = readRDS(paste0('../output/ImmuneEZ.V',vhat,'.center.resEZ.reQTL.rna6h.K',K,'.P',P,'.rds'))
length(get_significant_results(resEZ.rna6h))
```

We found `r round(length(get_significant_results(resEZ.rna6h))/length(eQTL.index.rna6h) * 100,2)`% [18%] of rna 6h eQTLs are reQTLs.

### RNA 90
```{r, echo=FALSE}
eQTL.index.rna90 = get_significant_results(resEZ, conditions = 7)
A.rna90 = rbind(c(1,0,0,0,0,0,-1))
row.names(A.rna90) = c('Ctrl-rna90')
```

```{r, echo=FALSE}
resEZ.rna90 = resEZ
eQTL.rna90 = subset.data(mash_data, eQTL.index.rna90)
resEZ.rna90$result = mash_compute_posterior_matrices(resEZ, eQTL.rna90, A=A.rna90, algorithm.version = 'R')
saveRDS(resEZ.rna90, 
        paste0('../output/ImmuneEZ.V',vhat,'.center.resEZ.reQTL.rna90.K',K,'.P',P,'.rds'))

```

```{r}
resEZ.rna90 = readRDS(paste0('../output/ImmuneEZ.V',vhat,'.center.resEZ.reQTL.rna90.K',K,'.P',P,'.rds'))
length(get_significant_results(resEZ.rna90))
```

We found `r round(length(get_significant_results(resEZ.rna90))/length(eQTL.index.rna90) * 100,2)`% [3%] of rna 90 eQTLs are reQTLs.

In the paper, they found 3-18% of cis eQTLs in each condition are reQTLs.

## Treatment specificity of reQTLs

### LPS 6h
```{r}
reQTL.index.lps6h = get_significant_results(resEZ.lps6h)
A.lps6hTRT = rbind(c(0,1,0,-1,0,0,0),
          c(0,1,0,0,0,-1,0))
row.names(A.lps6hTRT) = c('lps6h-mdp6h', 'lps6h-rna6h')
```
```{r}
resEZ.lps6hTRT = resEZ
reQTL.lps6h = subset.data(eQTL.lps6h, reQTL.index.lps6h)
resEZ.lps6hTRT$result = mash_compute_posterior_matrices(resEZ, reQTL.lps6h, A=A.lps6hTRT, algorithm.version = 'R')
saveRDS(resEZ.lps6hTRT, 
        paste0('../output/ImmuneEZ.V',vhat,'.center.resEZ.reQTL.lps6hTRT.K',K,'.P',P,'.rds'))

```

```{r}
resEZ.lps6hTRT = readRDS(paste0('../output/ImmuneEZ.V',vhat,'.center.resEZ.reQTL.lps6hTRT.K',K,'.P',P,'.rds'))
length(get_significant_results(resEZ.lps6hTRT))
```

We found `r round(length(get_significant_results(resEZ.lps6hTRT, conditions = 1))/length(reQTL.index.lps6h) * 100,2)`% [32%] lps6h reQTLs are stimulus specific compared with mdp6h, `r round(length(get_significant_results(resEZ.lps6hTRT, conditions = 2))/length(reQTL.index.lps6h) * 100,2)`% [34%] lps6h reQTLs are stimulus specific compared with rna6h.

### LPS 90
```{r, echo=FALSE}
reQTL.index.lps90 = get_significant_results(resEZ.lps90)
A.lps90TRT = rbind(c(0,0,1,0,-1,0,0),
                   c(0,0,1,0,0,0,-1))
row.names(A.lps90TRT) = c('lps90-mdp90', 'lps90-rna90')
```
```{r, echo=FALSE}
resEZ.lps90TRT = resEZ
reQTL.lps90 = subset.data(eQTL.lps90, reQTL.index.lps90)
resEZ.lps90TRT$result = mash_compute_posterior_matrices(resEZ, reQTL.lps90, A=A.lps90TRT, algorithm.version = 'R')
saveRDS(resEZ.lps90TRT, 
        paste0('../output/ImmuneEZ.V',vhat,'.center.resEZ.reQTL.lps90TRT.K',K,'.P',P,'.rds'))

```

```{r}
resEZ.lps90TRT = readRDS(paste0('../output/ImmuneEZ.V',vhat,'.center.resEZ.reQTL.lps90TRT.K',K,'.P',P,'.rds'))
length(get_significant_results(resEZ.lps90TRT))
```

We found `r round(length(get_significant_results(resEZ.lps90TRT, conditions = 1))/length(reQTL.index.lps90) * 100,2)`% [14%] lps 90min reQTLs are stimulus specific compared with mdp 90min, `r round(length(get_significant_results(resEZ.lps90TRT, conditions = 2))/length(reQTL.index.lps90) * 100,2)`% [51%] lps 90min reQTLs are stimulus specific compared with rna 90min.

### MDP 6h
```{r, echo=FALSE}
reQTL.index.mdp6h = get_significant_results(resEZ.mdp6h)
A.mdp6hTRT = rbind(c(0,-1,0,1,0,0,0),
                   c(0,0,0,1,0,-1,0))
row.names(A.mdp6hTRT) = c('mdp6h-lps6h', 'mdp6h-rna6h')
```
```{r, echo=FALSE}
resEZ.mdp6hTRT = resEZ
reQTL.mdp6h = subset.data(eQTL.mdp6h, reQTL.index.mdp6h)
resEZ.mdp6hTRT$result = mash_compute_posterior_matrices(resEZ, reQTL.mdp6h, A=A.mdp6hTRT, algorithm.version = 'R')
saveRDS(resEZ.mdp6hTRT, 
        paste0('../output/ImmuneEZ.V',vhat,'.center.resEZ.reQTL.mdp6hTRT.K',K,'.P',P,'.rds'))

```

```{r}
resEZ.mdp6hTRT = readRDS(paste0('../output/ImmuneEZ.V',vhat,'.center.resEZ.reQTL.mdp6hTRT.K',K,'.P',P,'.rds'))
length(get_significant_results(resEZ.mdp6hTRT))
```

We found `r round(length(get_significant_results(resEZ.mdp6hTRT, conditions = 1))/length(reQTL.index.mdp6h) * 100,2)`% [15%] mdp 6h reQTLs are stimulus specific compared with lps 6h, `r round(length(get_significant_results(resEZ.mdp6hTRT, conditions = 2))/length(reQTL.index.mdp6h) * 100,2)`% [13%] mdp 6h reQTLs are stimulus specific compared with rna 6h.

### MDP 90
```{r, echo=FALSE}
reQTL.index.mdp90 = get_significant_results(resEZ.mdp90)
A.mdp90TRT = rbind(c(0,0,-1,0,1,0,0),
                   c(0,0,0,0,1,0,-1))
row.names(A.mdp90TRT) = c('mdp90-lps90', 'mdp90-rna90')
```
```{r, echo=FALSE}
resEZ.mdp90TRT = resEZ
reQTL.mdp90 = subset.data(eQTL.mdp90, reQTL.index.mdp90)
resEZ.mdp90TRT$result = mash_compute_posterior_matrices(resEZ, reQTL.mdp90, A=A.mdp90TRT, algorithm.version = 'R')
saveRDS(resEZ.mdp90TRT, 
        paste0('../output/ImmuneEZ.V',vhat,'.center.resEZ.reQTL.mdp90TRT.K',K,'.P',P,'.rds'))

```

```{r}
resEZ.mdp90TRT = readRDS(paste0('../output/ImmuneEZ.V',vhat,'.center.resEZ.reQTL.mdp90TRT.K',K,'.P',P,'.rds'))
length(get_significant_results(resEZ.mdp90TRT))
```

We found `r round(length(get_significant_results(resEZ.mdp90TRT, conditions = 1))/length(reQTL.index.mdp90) * 100,2)`% [15%] mdp 90min reQTLs are stimulus specific compared with lps 90min, `r round(length(get_significant_results(resEZ.mdp90TRT, conditions = 2))/length(reQTL.index.mdp90) * 100,2)`% [46%] mdp 90min reQTLs are stimulus specific compared with rna 90min.

### RNA 6h
```{r, echo=FALSE}
reQTL.index.rna6h = get_significant_results(resEZ.rna6h)
A.rna6hTRT = rbind(c(0,-1,0,0,0,1,0),
                   c(0,0,0,-1,0,1,0))
row.names(A.rna6hTRT) = c('rna6h-lps6h', 'rna6h-mdp6h')
```
```{r, echo=FALSE}
resEZ.rna6hTRT = resEZ
reQTL.rna6h = subset.data(eQTL.rna6h, reQTL.index.rna6h)
resEZ.rna6hTRT$result = mash_compute_posterior_matrices(resEZ, reQTL.rna6h, A=A.rna6hTRT, algorithm.version = 'R')
saveRDS(resEZ.rna6hTRT, 
        paste0('../output/ImmuneEZ.V',vhat,'.center.resEZ.reQTL.rna6hTRT.K',K,'.P',P,'.rds'))

```

```{r}
resEZ.rna6hTRT = readRDS(paste0('../output/ImmuneEZ.V',vhat,'.center.resEZ.reQTL.rna6hTRT.K',K,'.P',P,'.rds'))
length(get_significant_results(resEZ.rna6hTRT))
```

We found `r round(length(get_significant_results(resEZ.rna6hTRT, conditions = 1))/length(reQTL.index.rna6h) * 100,2)`% [21%] rna 6h reQTLs are stimulus specific compared with lps 6h, `r round(length(get_significant_results(resEZ.rna6hTRT, conditions = 2))/length(reQTL.index.rna6h) * 100,2)`% [45%] rna 6h reQTLs are stimulus specific compared with mdp 6h.

### RNA 90
```{r, echo=FALSE}
reQTL.index.rna90 = get_significant_results(resEZ.rna90)
A.rna90TRT = rbind(c(0,0,-1,0,0,0,1),
                   c(0,0,0,0,-1,0,1))
row.names(A.rna90TRT) = c('rna90-lps90', 'rna90-mdp90')
```
```{r, echo=FALSE}
resEZ.rna90TRT = resEZ
reQTL.rna90 = subset.data(eQTL.rna90, reQTL.index.rna90)
resEZ.rna90TRT$result = mash_compute_posterior_matrices(resEZ, reQTL.rna90, A=A.rna90TRT, algorithm.version = 'R')
saveRDS(resEZ.rna90TRT, 
        paste0('../output/ImmuneEZ.V',vhat,'.center.resEZ.reQTL.rna90TRT.K',K,'.P',P,'.rds'))

```

```{r}
resEZ.rna90TRT = readRDS(paste0('../output/ImmuneEZ.V',vhat,'.center.resEZ.reQTL.rna90TRT.K',K,'.P',P,'.rds'))
length(get_significant_results(resEZ.rna90TRT))
```

We found `r round(length(get_significant_results(resEZ.rna90TRT, conditions = 1))/length(reQTL.index.rna90) * 100,2)`% [38%] rna 90min reQTLs are stimulus specific compared with lps 90min, `r round(length(get_significant_results(resEZ.rna90TRT, conditions = 2))/length(reQTL.index.rna90) * 100,2)`% [29%] rna 90min reQTLs are stimulus specific compared with mdp 90min.

## Time point specificity of reQTLs

### LPS 6h
```{r}
A.lps6hTime = rbind(c(0,1,-1,0,0,0,0))
row.names(A.lps6hTime) = c('lps6h-lps90')
```
```{r}
resEZ.lps6hTime = resEZ
resEZ.lps6hTime$result = mash_compute_posterior_matrices(resEZ, reQTL.lps6h , A=A.lps6hTime, algorithm.version = 'R')
saveRDS(resEZ.lps6hTime, 
        paste0('../output/ImmuneEZ.V',vhat,'.center.resEZ.reQTL.lps6hTime.K',K,'.P',P,'.rds'))

```

```{r}
resEZ.lps6hTime = readRDS(paste0('../output/ImmuneEZ.V',vhat,'.center.resEZ.reQTL.lps6hTime.K',K,'.P',P,'.rds'))
length(get_significant_results(resEZ.lps6hTime))
```

We found `r round(length(get_significant_results(resEZ.lps6hTime, conditions = 1))/length(reQTL.index.lps6h) * 100,2)`% [45%] lps6h reQTLs are time point specific compared with lps90min.

### LPS 90
```{r, echo=FALSE}
A.lps90Time = rbind(c(0,-1,1,0,0,0,0))
row.names(A.lps90Time) = c('lps90-lps6h')
```
```{r, echo=FALSE}
resEZ.lps90Time = resEZ
resEZ.lps90Time$result = mash_compute_posterior_matrices(resEZ, reQTL.lps90, A=A.lps90Time, algorithm.version = 'R')
saveRDS(resEZ.lps90Time, 
        paste0('../output/ImmuneEZ.V',vhat,'.center.resEZ.reQTL.lps90Time.K',K,'.P',P,'.rds'))

```

```{r}
resEZ.lps90Time = readRDS(paste0('../output/ImmuneEZ.V',vhat,'.center.resEZ.reQTL.lps90Time.K',K,'.P',P,'.rds'))
length(get_significant_results(resEZ.lps90Time))
```

We found `r round(length(get_significant_results(resEZ.lps90Time, conditions = 1))/length(reQTL.index.lps90) * 100,2)`% [36%] lps 90min reQTLs are time point specific compared with lps6h.

### MDP 6h
```{r, echo=FALSE}
A.mdp6hTime = rbind(c(0,0,0,1,-1,0,0))
row.names(A.mdp6hTime) = c('mdp6h-mdp90')
```
```{r, echo=FALSE}
resEZ.mdp6hTime = resEZ
resEZ.mdp6hTime$result = mash_compute_posterior_matrices(resEZ, reQTL.mdp6h, A=A.mdp6hTime, algorithm.version = 'R')
saveRDS(resEZ.mdp6hTime, 
        paste0('../output/ImmuneEZ.V',vhat,'.center.resEZ.reQTL.mdp6hTime.K',K,'.P',P,'.rds'))

```

```{r}
resEZ.mdp6hTime = readRDS(paste0('../output/ImmuneEZ.V',vhat,'.center.resEZ.reQTL.mdp6hTime.K',K,'.P',P,'.rds'))
length(get_significant_results(resEZ.mdp6hTime))
```

We found `r round(length(get_significant_results(resEZ.mdp6hTRT, conditions = 1))/length(reQTL.index.mdp6h) * 100,2)`% [40%] mdp 6h reQTLs are time point specific compared with mdp 90min.

### MDP 90
```{r, echo=FALSE}
A.mdp90Time = rbind(c(0,0,0,-1,1,0,0))
row.names(A.mdp90Time) = c('mdp90-mdp6h')
```
```{r, echo=FALSE}
resEZ.mdp90Time = resEZ
resEZ.mdp90Time$result = mash_compute_posterior_matrices(resEZ, reQTL.mdp90, A=A.mdp90Time, algorithm.version = 'R')
saveRDS(resEZ.mdp90Time, 
        paste0('../output/ImmuneEZ.V',vhat,'.center.resEZ.reQTL.mdp90Time.K',K,'.P',P,'.rds'))

```

```{r}
resEZ.mdp90Time = readRDS(paste0('../output/ImmuneEZ.V',vhat,'.center.resEZ.reQTL.mdp90Time.K',K,'.P',P,'.rds'))
length(get_significant_results(resEZ.mdp90Time))
```

We found `r round(length(get_significant_results(resEZ.mdp90Time, conditions = 1))/length(reQTL.index.mdp90) * 100,2)`% [38%] mdp 90min reQTLs time point specific compared with mdp 6h.

### RNA 6h
```{r, echo=FALSE}
A.rna6hTime = rbind(c(0,0,0,0,0,1,-1))
row.names(A.rna6hTime) = c('rna6h-rna90')
```
```{r, echo=FALSE}
resEZ.rna6hTime = resEZ
resEZ.rna6hTime$result = mash_compute_posterior_matrices(resEZ, reQTL.rna6h, A=A.rna6hTime, algorithm.version = 'R')
saveRDS(resEZ.rna6hTime, 
        paste0('../output/ImmuneEZ.V',vhat,'.center.resEZ.reQTL.rna6hTime.K',K,'.P',P,'.rds'))

```

```{r}
resEZ.rna6hTime = readRDS(paste0('../output/ImmuneEZ.V',vhat,'.center.resEZ.reQTL.rna6hTime.K',K,'.P',P,'.rds'))
length(get_significant_results(resEZ.rna6hTime))
```

We found `r round(length(get_significant_results(resEZ.rna6hTime, conditions = 1))/length(reQTL.index.rna6h) * 100,2)`% [64%] rna 6h reQTLs are time point specific compared with rna 90min.

### RNA 90
```{r, echo=FALSE}
A.rna90Time = rbind(c(0,0,0,0,0,-1,1))
row.names(A.rna90Time) = c('rna90-rna6h')
```
```{r, echo=FALSE}
resEZ.rna90Time = resEZ
resEZ.rna90Time$result = mash_compute_posterior_matrices(resEZ, reQTL.rna90, A=A.rna90Time, algorithm.version = 'R')
saveRDS(resEZ.rna90Time, 
        paste0('../output/ImmuneEZ.V',vhat,'.center.resEZ.reQTL.rna90Time.K',K,'.P',P,'.rds'))

```

```{r}
resEZ.rna90Time = readRDS(paste0('../output/ImmuneEZ.V',vhat,'.center.resEZ.reQTL.rna90Time.K',K,'.P',P,'.rds'))
length(get_significant_results(resEZ.rna90Time))
```

We found `r round(length(get_significant_results(resEZ.rna90Time, conditions = 1))/length(reQTL.index.rna90) * 100,2)`% [32%] rna 90min reQTLs are time point specific compared with rna 6h.

# Session information

<!-- Insert the session information into the document -->
```{r session-info}
```
