---
title: "Immune Data Mash"
author: "Yuxin Zou"
date: 2017-11-15
output: html_document
---
```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
```

<!-- Update knitr chunk options -->
```{r knitr-opts-chunk, include=FALSE}
```

<!-- Insert the date the file was last updated -->
```{r last-updated, echo=FALSE, results='asis'}
```

<!-- Insert the code version (Git commit SHA1) if Git repository exists and R
 package git2r is installed -->
```{r code-version, echo=FALSE, results='asis'}
```

# Set up the data
```{r}
# Load required packages
library(mashr); library(ExtremeDeconvolution); library(flashr2)
```
```{r}
# read data
data = readRDS('../data/ImmuneQTLSummary.4MASH.rds')
data$max$se = data$max$beta/data$max$z
data$null$se = data$null$beta / data$null$z

# set parameters
K = 10
P = 5
vhat = 1
cov = 'xtx'
```
# Column-centered Z scores
$$ \tilde{Z}_{n\times 7} = Z-[\mu_{1}, \cdots, \mu_{7}]$$
```{r}
D.center = apply(as.matrix(data$max$z), 2, function(x) x - mean(x))
mash_data_center = mashr::set_mash_data(Bhat = as.matrix(D.center), 
                                        Shat = matrix(1, nrow(data$max$z),
                                                      ncol(data$max$z)))
```

# Using Flash to estimate the covariance

Using greedy algorithm, we can set the variance structure for the residuals. The available types of variance structure are 'by_column' and 'constant'. Since the columns of the data are different treatments. It is more reasonable to use 'by_column' structure, rather than 'constant'. We apply flash on 
$$ \tilde{Z} = LF' + E $$
where F is $7 \times K$, L is $n \times K$, E is $n\times7$.

```{r, warning = FALSE}
# use D.center
mash_data_flash = flash_set_data(as.matrix(D.center))
f_greedy = flash_add_greedy(mash_data_flash, Kmax=K, var_type = 'by_column')
```

Backfitting
```{r, warning = FALSE}
f_greedy_bf = flash_backfit(mash_data_flash,f_greedy, var_type = 'by_column')
F_flash = flash_get_f(f_greedy_bf)
L_flash = flash_get_l(f_greedy_bf)

saveRDS(list(f_greedy = f_greedy,
             f = f_greedy_bf,
             F_flash = F_flash,
             L_flash = L_flash),
        paste0("../output/Immune.flash2.center.greedy.K", K,".rds"))
```

## Flashr result

Check fit of Flash greedy:
```{r}
FlashResult = readRDS('../output/Immune.flash2.center.greedy.K10.rds')
flash_get_pve(FlashResult$f_greedy)
flash_get_sizes(FlashResult$f_greedy)

F_greedy = flash_get_f(FlashResult$f_greedy)
row.names(F_greedy) = c("ctrl", "lps6h", "lps90", "mdp6h", "mdp90", "rna6h", "rna90")
barplot(F_greedy[,1], las=2, main='Loading 1')
barplot(F_greedy[,2], las=2, main='Loading 2')
barplot(F_greedy[,3], las=2, main='Loading 3')
barplot(F_greedy[,4], las=2, main='Loading 4')
barplot(F_greedy[,5], las=2, main='Loading 5')
```

Check fit of Flash greedy backfitting:

The first factor explains the main proportion of variance in effects.
```{r}
flash_get_pve(FlashResult$f)
flash_get_sizes(FlashResult$f)
```

The first factor is the overall summary of treatment effects.
```{r}
row.names(FlashResult$F_flash) = c("ctrl", "lps6h", "lps90", "mdp6h", "mdp90", "rna6h", "rna90")
barplot(FlashResult$F_flash[,1], las=2, main='Loading 1')
barplot(FlashResult$F_flash[,2], las=2, main='Loading 2')
barplot(FlashResult$F_flash[,3], las=2, main='Loading 3')
barplot(FlashResult$F_flash[,4], las=2, main='Loading 4')
barplot(FlashResult$F_flash[,5], las=2, main='Loading 5')
# dominated by rna6h
```

The loading structure is not sparse. 

# Create and refine multi-rank covariance matrices

Here we create 3 covariance matrices:

* Flash (rank 5, previously computed)
  $$ \tilde{Z} = LF' + E $$
  $$ U = \frac{1}{n} (LF')'(LF') $$
    + plus single rank Flashs for each factor
    The 5 matrices $F_{q}L_{q}' L_{q} F_{q}'$
    
* PCA (rank 5, to be computed)
    + plus single rank PCAs
    
* Optionally
    + Empirical covariance
    
and apply `Extreme Deconvolution` to refine these matrices. We observed that Extreme Deconvolution perserves rank.

Additionally we include 2 other types of covariance matrices:

* canonical configurations (aka `bmalite`)

* simple heterogeneity models

```{r}
FlashResult = readRDS('../output/Immune.flash2.center.greedy.K10.rds')
Flash_res = flash_get_lf(FlashResult$f)

U.flash = c(mashr::cov_from_factors(t(as.matrix(FlashResult$F_flash[,1:5])), "Flash"), 
            list("tFlash" = t(Flash_res) %*% Flash_res / nrow(data$max$z)))

# Canonical
U.can = cov_canonical(mash_data_center) 

# PCA matrices
U.pca = cov_pca(mash_data_center, P)

# Emperical data matrices
# Denoised data-driven matrices
U.dd = c(U.flash, U.pca, list("XX" = t(D.center) %*% D.center / nrow(data$max$z)))

mash_data = mashr::set_mash_data(Bhat = as.matrix(data$max$z), 
                                 Shat = matrix(1, nrow(data$max$z),
                                               ncol(data$max$z)))

U.ed = cov_ed(mash_data, U.dd)
# save Covariance matrix
saveRDS(list(Ulist = c(U.ed, U.can), DD_raw = U.dd), 
        paste0('../output/Immune.U.center.xtx.K',K,'.P',P,'.rds'))

```

# Fit mash model

Using a random null set, the cell below computes the weights for input covariance matrices (priors) in MASH mixture. The output contains matrix of log-likelihoods as well as weights learned from the hierarchical model.

```{r}
if (vhat == 1) {
  V = cor(data$null$z[which(apply(abs(data$null$z),1, max) < 2),])
} else {
  V = diag(ncol(data$null$z))
}
mash_data = mashr::set_mash_data(Bhat = as.matrix(data$null$beta), 
                                 Shat = as.matrix(data$null$se), 
                                 V=as.matrix(V), alpha=1)

Ulist = readRDS('../output/Immune.U.center.xtx.K10.P5.rds')$Ulist
saveRDS(mashr::mash(mash_data, Ulist, outputlevel = 1), 
        paste0('../output/ImmuneEZ.V',vhat,'.center.mash_model.K',K,'.P',P,'.rds'))

```

# Session information

<!-- Insert the session information into the document -->
```{r session-info}
```
