---
title: "Immune Data Mash Analysis EE V1 Results"
author: "Yuxin Zou"
date: 2017-11-16
output: html_document
---

```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
knitr::read_chunk('../code/subset.data.R')
```

<!-- Update knitr chunk options -->
```{r knitr-opts-chunk, include=FALSE}
```

<!-- Insert the date the file was last updated -->
```{r last-updated, echo=FALSE, results='asis'}
```

<!-- Insert the code version (Git commit SHA1) if Git repository exists and R
 package git2r is installed -->
```{r code-version, echo=FALSE, results='asis'}
```

# Set up data
```{r}
library(lattice)
library(ggplot2)
library(colorRamps)
library(mashr)
library(corrplot)
data = readRDS('../data/ImmuneQTLSummary.4MASH.rds')
data$max$se = data$max$beta/data$max$z
data$null$se = data$null$beta / data$null$z

K = 10
P = 5
vhat = 1
```

```{r}
if (vhat == 1) {
  V = cor(data$null$z[which(apply(abs(data$null$z),1, max) < 2),])
} else {
  V = diag(ncol(data$null$z))
}
mash_data = mashr::set_mash_data(Bhat = as.matrix(data$max$beta), 
                                 Shat = as.matrix(data$max$se), 
                                 V = as.matrix(V), 
                                 alpha = 0)
```

# MASH results

```{r}
# EE
resEE = readRDS('../output/ImmuneEE.V1.center.mash_model.K10.P5.rds')
resEE$result = readRDS('../output/ImmuneEE.V1.center.mash_posterior.K10.P5.rds')
```

# MASH model fit

The log-likelihood of fit is
```{r} 
get_loglik(resEE)
```

Here is a plot of weights learned.

```{r}
options(repr.plot.width=12, repr.plot.height=4)
barplot(get_estimated_pi(resEE), las = 2, cex.names = 0.7)
```

Here is a visualization for Flash4, which capture `r round(get_estimated_pi(resEE)['ED_Flash_4']*100,4)`% mixture component in these data, (via correlation heatmap):

```{r}
x           <- cov2cor(resEE$fitted_g$Ulist[["ED_Flash_4"]])
x[x > 1]    <- 1
x[x < -1]   <- -1
colnames(x) <- colnames(get_lfsr(resEE))
rownames(x) <- colnames(x)
corrplot.mixed(x, tl.pos="d",upper='color',cl.lim=c(-1,1), upper.col=colorRampPalette(rev(c("#D73027","#FC8D59","#FEE090","#FFFFBF",
                               "#E0F3F8","#91BFDB","#4575B4")))(40),
               tl.cex=1.2)
```

Here is a visualization for PCA5, which capture `r get_estimated_pi(resEE)['ED_PCA_5']*100`% mixture component in these data, (via correlation heatmap):

```{r}
x           <- cov2cor(resEE$fitted_g$Ulist[["ED_PCA_5"]])
x[x > 1]    <- 1
x[x < -1]   <- -1
colnames(x) <- colnames(get_lfsr(resEE))
rownames(x) <- colnames(x)
corrplot.mixed(x, tl.pos="d",upper='color',cl.lim=c(-1,1), upper.col=colorRampPalette(rev(c("#D73027","#FC8D59","#FEE090","#FFFFBF",
                               "#E0F3F8","#91BFDB","#4575B4")))(40),
               tl.cex=1.2)
```

Next we perform SVD on the PCA 5 based covariance matrix, and plot the top eigen vector.

```{r}
svd.out = svd(resEE$fitted_g$Ulist[["ED_PCA_5"]])
v = svd.out$v
colnames(v) = colnames(get_lfsr(resEE))
rownames(v) = colnames(v)
options(repr.plot.width=10, repr.plot.height=5)
for (j in 1:1)
  barplot(v[,j]/v[,j][which.max(abs(v[,j]))], cex.names = 0.7,
          las = 2, main = paste0("EigenVector ", j, " for PCA-based covariance matrix"))
```

```{r}
head(get_significant_results(resEE))
```

## Examples of how `mash` uses patterns of sharing to inform estimated effect:

* Original estimates
```{r echo=FALSE}
# raw effect
stronggene = data.frame(data$max$beta[19734,])
colnames(stronggene) = 'EffectSize'
stronggene$Group = row.names(stronggene)
stronggene$se = data.frame(data$max$se[19734, ])
ggplot(stronggene, aes(y = EffectSize, x = Group, color=Group)) + 
  geom_point() + ylim(c(-0.3, -0.1)) +
  geom_errorbar(aes(ymin=EffectSize-1.96*se, ymax=EffectSize+1.96*se), width=0.4) + 
  theme_bw(base_size=12) + coord_flip() + ggtitle('ILMN_3237396_rs4776354')
```

* `MASH` estimates

```{r echo=FALSE}
# Improved
stronggenePost = data.frame(resEE$result$PosteriorMean[19734,])
colnames(stronggenePost) = 'EffectSize'
stronggenePost$Group = row.names(stronggenePost)
stronggenePost$se = resEE$result$PosteriorSD[19734,]
ggplot(stronggenePost, aes(y = EffectSize, x = Group, color=Group)) + 
  geom_point() + ylim(c(-0.3, -0.1)) +
  geom_errorbar(aes(ymin=EffectSize-1.96*se, ymax=EffectSize+1.96*se), width=0.4) + 
  theme_bw(base_size=12) + coord_flip() + ggtitle('ILMN_3237396_rs4776354')
```

Here is one example of shinkage:

* Original estimates
```{r echo=FALSE}
# raw effect
stronggene = data.frame(data$max$beta[1,])
colnames(stronggene) = 'EffectSize'
stronggene$Group = row.names(stronggene)
stronggene$se = data$max$se[1,]
ggplot(stronggene, aes(y = EffectSize, x = Group, color=Group)) + 
  geom_point() + geom_hline(yintercept = 0) + 
  geom_errorbar(aes(ymin=EffectSize-1.96*se, ymax=EffectSize+1.96*se), width=0.4) + 
  theme_bw(base_size=12) + coord_flip() + ggtitle('ILMN_1343291_rs13216349')
```

* `MASH` estimates

```{r echo=FALSE}
# Improved
stronggenePost = data.frame(resEE$result$PosteriorMean[1,])
colnames(stronggenePost) = 'EffectSize'
stronggenePost$Group = row.names(stronggenePost)
stronggenePost$se = resEE$result$PosteriorSD[1,]
ggplot(stronggenePost, aes(y = EffectSize, x = Group, color=Group)) + 
  geom_point() + geom_hline(yintercept = 0) + 
  geom_errorbar(aes(ymin=EffectSize-1.96*se, ymax=EffectSize+1.96*se), width=0.4) + 
  theme_bw(base_size=12) + coord_flip() + ggtitle('ILMN_1343291_rs13216349')
```

The estimated effects are closer to 0.
<!--
* Original estimates
```{r echo=FALSE}
# raw effect
stronggene = data.frame(data$max$beta[2,])
colnames(stronggene) = 'EffectSize'
stronggene$Group = row.names(stronggene)
stronggene$se = data$max$se[2,]
ggplot(stronggene, aes(y = EffectSize, x = Group, color=Group)) + 
  geom_point() + geom_hline(yintercept = 0) + 
  geom_errorbar(aes(ymin=EffectSize-1.96*se, ymax=EffectSize+1.96*se), width=0.4) + 
  theme_bw(base_size=12) + coord_flip() + ggtitle('ILMN_1343295_rs80259531')
```

* `MASH` estimates

```{r echo=FALSE}
# Improved
stronggenePost = data.frame(resEE$result$PosteriorMean[2,])
colnames(stronggenePost) = 'EffectSize'
stronggenePost$Group = row.names(stronggenePost)
stronggenePost$se = resEE$result$PosteriorSD[2,]
ggplot(stronggenePost, aes(y = EffectSize, x = Group, color=Group)) + 
  geom_point() + geom_hline(yintercept = 0) + 
  geom_errorbar(aes(ymin=EffectSize-1.96*se, ymax=EffectSize+1.96*se), width=0.4) + 
  theme_bw(base_size=12) + coord_flip() + ggtitle('ILMN_1343295_rs80259531')
```

All estimated effects become similar.
-->

Pairwise sharing

```{r}
x           <- get_pairwise_sharing(resEE)
colnames(x) <- colnames(get_lfsr(resEE))
rownames(x) <- colnames(x)
x <- x[rev(rownames(x)),rev(colnames(x))]
x[lower.tri(x)] <- NA
clrs <- colorRampPalette(rev(c("#D73027","#FC8D59","#FEE090","#FFFFBF",
                               "#E0F3F8","#91BFDB","#4575B4")))(64)
n <- nrow(x)
options(repr.plot.width=9, repr.plot.height=9)
print(levelplot(x[n:1,],col.regions = clrs,xlab = "",ylab = "",
                colorkey = TRUE, at = seq(0.7,1,length.out = 64),
                scales = list(cex = 0.5,x = list(rot = 45))))

```

# Compare with original paper

## eQTLs
Among the 21485 top SNPs, `MASH` found `r length(get_significant_results(resEE))` to be significant in at least one treatment. We refer to these as the 'top eQTLs'.

Using `MASH`, we found `r length(get_significant_results(resEE, conditions = 1))` genes with an eQTL in control, `r length(get_significant_results(resEE, conditions = 2))` genes with an eQTL in lps6h, `r length(get_significant_results(resEE, conditions = 3))` genes with an eQTL in lps90, `r length(get_significant_results(resEE, conditions = 4))` genes with an eQTL in mdp6h, `r length(get_significant_results(resEE, conditions = 5))` genes with an eQTL in mdp90, `r length(get_significant_results(resEE, conditions = 6))` genes with an eQTL in rna6h, `r length(get_significant_results(resEE, conditions = 7))` genes with an eQTL in rna90.

In the original paper, they identified 717-1653 genes with an eQTL in each condition. So, we found more genes with an eQTL using `MASH`.

```{r echo=FALSE}
comm = Reduce(intersect, list(get_significant_results(resEE, conditions=1),
                       get_significant_results(resEE, conditions=2),
                       get_significant_results(resEE, conditions=3),
                       get_significant_results(resEE, conditions=4),
                       get_significant_results(resEE, conditions=5),
                       get_significant_results(resEE, conditions=6),
                       get_significant_results(resEE, conditions=7)))
```

There are `r length(comm)` top eQTLs with significant effects among all treatments.

<!---
## Find genes specific to one treatment

```{r}
# function to find gene specific to condition i
Geneto1Cond = function(resEE, cond){
  conditiontotal = seq(1,ncol(resEE$result$PosteriorMean))
  OtherCond = conditiontotal[-cond]
  for(i in 1:6){
    if(i == 1){
      setd = setdiff(get_significant_results(resEE, conditions=cond), 
                     get_significant_results(resEE, conditions=OtherCond[i]))
    }
    else{
      setd = setdiff(setd,
                     get_significant_results(resEE, conditions=OtherCond[i]))
    }
    
  }
  return(setd)
}
```

```{r}
GeneNames = row.names(data$max$beta)
for(i in 1:7){
  cat('Gene has significant effect only in condition ', i, ': Total = ', length(GeneNames[Geneto1Cond(resEE,i)]), '\n', GeneNames[Geneto1Cond(resEE,i)], '\n')
  cat('\n')
}
```
-->

## reQTLs
Find genes having $\beta_{Trt}$ significantly different from $\beta_{Ctrl}$, among the top eQTLs. The number in [] is the result from the paper. Note that, there are only percentages provided in the paper. Since the number of top eQTLs we found are different, the percentage may not directly comparable.

```{r subset.data}
```

### LPS 6h
```{r}
eQTL.index.lps6h = get_significant_results(resEE, conditions = 2)
A.lps6h = rbind(c(1,-1,0,0,0,0,0))
row.names(A.lps6h) = c('Ctrl-lps6h')
```

```{r}
resEE.lps6h = resEE
eQTL.lps6h = subset.data(mash_data, eQTL.index.lps6h)
resEE.lps6h$result = mash_compute_posterior_matrices(resEE, eQTL.lps6h, A=A.lps6h, algorithm.version = 'R')
saveRDS(resEE.lps6h, 
        paste0('../output/ImmuneEE.V',vhat,'.center.resEE.lps6h.K',K,'.P',P,'.rds'))

```

```{r}
resEE.lps6h = readRDS(paste0('../output/ImmuneEE.V',vhat,'.center.resEE.lps6h.K',K,'.P',P,'.rds'))
length(get_significant_results(resEE.lps6h))
```

Using `MASH`, we found `r round(length(get_significant_results(resEE.lps6h))/length(eQTL.index.lps6h) * 100,2)`% [17%] of lps 6h eQTLs are reQTLs.

### LPS 90
```{r, echo=FALSE}
eQTL.index.lps90 = get_significant_results(resEE, conditions = 3)
A.lps90 = rbind(c(1,0,-1,0,0,0,0))
row.names(A.lps90) = c('Ctrl-lps90')
```

```{r, echo=FALSE}
resEE.lps90 = resEE
eQTL.lps90 = subset.data(mash_data, eQTL.index.lps90)
resEE.lps90$result = mash_compute_posterior_matrices(resEE, eQTL.lps90, A=A.lps90, algorithm.version = 'R')
saveRDS(resEE.lps90, 
        paste0('../output/ImmuneEE.V',vhat,'.center.resEE.lps90.K',K,'.P',P,'.rds'))

```

```{r}
resEE.lps90 = readRDS(paste0('../output/ImmuneEE.V',vhat,'.center.resEE.lps90.K',K,'.P',P,'.rds'))
length(get_significant_results(resEE.lps90))
```

We found `r round(length(get_significant_results(resEE.lps90))/length(eQTL.index.lps90) * 100,2)`% [15%] of lps 90 eQTLs are reQTLs.

### MDP 6h
```{r, echo=FALSE}
eQTL.index.mdp6h = get_significant_results(resEE, conditions = 4)
A.mdp6h = rbind(c(1,0,0,-1,0,0,0))
row.names(A.mdp6h) = c('Ctrl-mdp6h')
```

```{r, echo=FALSE}
resEE.mdp6h = resEE
eQTL.mdp6h = subset.data(mash_data, eQTL.index.mdp6h)
resEE.mdp6h$result = mash_compute_posterior_matrices(resEE, eQTL.mdp6h, A=A.mdp6h, algorithm.version = 'R')
saveRDS(resEE.mdp6h, 
        paste0('../output/ImmuneEE.V',vhat,'.center.resEE.mdp6h.K',K,'.P',P,'.rds'))

```

```{r}
resEE.mdp6h = readRDS(paste0('../output/ImmuneEE.V',vhat,'.center.resEE.mdp6h.K',K,'.P',P,'.rds'))
length(get_significant_results(resEE.mdp6h))
```

We found `r round(length(get_significant_results(resEE.mdp6h))/length(eQTL.index.mdp6h) * 100,2)`% [9%] of mdp 6h eQTLs are reQTLs.

### MDP 90
```{r, echo=FALSE}
eQTL.index.mdp90 = get_significant_results(resEE, conditions = 5)
A.mdp90 = rbind(c(1,0,0,0,-1,0,0))
row.names(A.mdp90) = c('Ctrl-mdp90')
```

```{r, echo=FALSE}
resEE.mdp90 = resEE
eQTL.mdp90 = subset.data(mash_data, eQTL.index.mdp90)
resEE.mdp90$result = mash_compute_posterior_matrices(resEE, eQTL.mdp90, A=A.mdp90, algorithm.version = 'R')
saveRDS(resEE.mdp90, 
        paste0('../output/ImmuneEE.V',vhat,'center.resEE.mdp90.K',K,'.P',P,'.rds'))

```

```{r}
resEE.mdp90 = readRDS(paste0('../output/ImmuneEE.V',vhat,'center.resEE.mdp90.K',K,'.P',P,'.rds'))
length(get_significant_results(resEE.mdp90))
```

We found `r round(length(get_significant_results(resEE.mdp90))/length(eQTL.index.mdp90) * 100,2)`% [9%] of mdp 90 eQTLs are reQTLs.

### RNA 6h
```{r, echo=FALSE}
eQTL.index.rna6h = get_significant_results(resEE, conditions = 6)
A.rna6h = rbind(c(1,0,0,0,0,-1,0))
row.names(A.rna6h) = c('Ctrl-rna6h')
```

```{r, echo=FALSE}
resEE.rna6h = resEE
eQTL.rna6h = subset.data(mash_data, eQTL.index.rna6h)
resEE.rna6h$result = mash_compute_posterior_matrices(resEE, eQTL.rna6h, A=A.rna6h, algorithm.version = 'R')
saveRDS(resEE.rna6h, 
        paste0('../output/ImmuneEE.V',vhat,'.center.resEE.rna6h.K',K,'.P',P,'.rds'))

```

```{r}
resEE.rna6h = readRDS(paste0('../output/ImmuneEE.V',vhat,'.center.resEE.rna6h.K',K,'.P',P,'.rds'))
length(get_significant_results(resEE.rna6h))
```

We found `r round(length(get_significant_results(resEE.rna6h))/length(eQTL.index.rna6h) * 100,2)`% [18%] of rna 6h eQTLs are reQTLs.

### RNA 90
```{r, echo=FALSE}
eQTL.index.rna90 = get_significant_results(resEE, conditions = 7)
A.rna90 = rbind(c(1,0,0,0,0,0,-1))
row.names(A.rna90) = c('Ctrl-rna90')
```

```{r, echo=FALSE}
resEE.rna90 = resEE
eQTL.rna90 = subset.data(mash_data, eQTL.index.rna90)
resEE.rna90$result = mash_compute_posterior_matrices(resEE, eQTL.rna90, A=A.rna90, algorithm.version = 'R')
saveRDS(resEE.rna90, 
        paste0('../output/ImmuneEE.V',vhat,'.center.resEE.rna90.K',K,'.P',P,'.rds'))

```

```{r}
resEE.rna90 = readRDS(paste0('../output/ImmuneEE.V',vhat,'.center.resEE.rna90.K',K,'.P',P,'.rds'))
length(get_significant_results(resEE.rna90))
```

We found `r round(length(get_significant_results(resEE.rna90))/length(eQTL.index.rna90) * 100,2)`% [3%] of rna 90 eQTLs are reQTLs.

In the paper, they found 3-18% of cis eQTLs in each condition are reQTLs.

## Treatment specificity of reQTLs

### LPS 6h
```{r}
reQTL.index.lps6h = get_significant_results(resEE.lps6h)
A.lps6hTRT = rbind(c(0,1,0,-1,0,0,0),
          c(0,1,0,0,0,-1,0))
row.names(A.lps6hTRT) = c('lps6h-mdp6h', 'lps6h-rna6h')
```
```{r}
resEE.lps6hTRT = resEE
reQTL.lps6h = subset.data(eQTL.lps6h, reQTL.index.lps6h)
resEE.lps6hTRT$result = mash_compute_posterior_matrices(resEE, reQTL.lps6h, A=A.lps6hTRT, algorithm.version = 'R')
saveRDS(resEE.lps6hTRT, 
        paste0('../output/ImmuneEE.V',vhat,'.center.resEE.lps6hTRT.K',K,'.P',P,'.rds'))

```

```{r}
resEE.lps6hTRT = readRDS(paste0('../output/ImmuneEE.V',vhat,'.center.resEE.lps6hTRT.K',K,'.P',P,'.rds'))
length(get_significant_results(resEE.lps6hTRT))
```

We found `r round(length(get_significant_results(resEE.lps6hTRT, conditions = 1))/length(reQTL.index.lps6h) * 100,2)`% [32%] lps6h reQTLs are stimulus specific compared with mdp6h, `r round(length(get_significant_results(resEE.lps6hTRT, conditions = 2))/length(reQTL.index.lps6h) * 100,2)`% [34%] lps6h reQTLs are stimulus specific compared with rna6h.

### LPS 90
```{r, echo=FALSE}
reQTL.index.lps90 = get_significant_results(resEE.lps90)
A.lps90TRT = rbind(c(0,0,1,0,-1,0,0),
                   c(0,0,1,0,0,0,-1))
row.names(A.lps90TRT) = c('lps90-mdp90', 'lps90-rna90')
```
```{r, echo=FALSE}
resEE.lps90TRT = resEE
reQTL.lps90 = subset.data(eQTL.lps90, reQTL.index.lps90)
resEE.lps90TRT$result = mash_compute_posterior_matrices(resEE, reQTL.lps90, A=A.lps90TRT, algorithm.version = 'R')
saveRDS(resEE.lps90TRT, 
        paste0('../output/ImmuneEE.V',vhat,'.center.resEE.lps90TRT.K',K,'.P',P,'.rds'))

```

```{r}
resEE.lps90TRT = readRDS(paste0('../output/ImmuneEE.V',vhat,'.center.resEE.lps90TRT.K',K,'.P',P,'.rds'))
length(get_significant_results(resEE.lps90TRT))
```

We found `r round(length(get_significant_results(resEE.lps90TRT, conditions = 1))/length(reQTL.index.lps90) * 100,2)`% [14%] lps 90min reQTLs are stimulus specific compared with mdp 90min, `r round(length(get_significant_results(resEE.lps90TRT, conditions = 2))/length(reQTL.index.lps90) * 100,2)`% [51%] lps 90min reQTLs are stimulus specific compared with rna 90min.

### MDP 6h
```{r, echo=FALSE}
reQTL.index.mdp6h = get_significant_results(resEE.mdp6h)
A.mdp6hTRT = rbind(c(0,-1,0,1,0,0,0),
                   c(0,0,0,1,0,-1,0))
row.names(A.mdp6hTRT) = c('mdp6h-lps6h', 'mdp6h-rna6h')
```
```{r, echo=FALSE}
resEE.mdp6hTRT = resEE
reQTL.mdp6h = subset.data(eQTL.mdp6h, reQTL.index.mdp6h)
resEE.mdp6hTRT$result = mash_compute_posterior_matrices(resEE, reQTL.mdp6h, A=A.mdp6hTRT, algorithm.version = 'R')
saveRDS(resEE.mdp6hTRT, 
        paste0('../output/ImmuneEE.V',vhat,'.center.resEE.mdp6hTRT.K',K,'.P',P,'.rds'))

```

```{r}
resEE.mdp6hTRT = readRDS(paste0('../output/ImmuneEE.V',vhat,'.center.resEE.mdp6hTRT.K',K,'.P',P,'.rds'))
length(get_significant_results(resEE.mdp6hTRT))
```

We found `r round(length(get_significant_results(resEE.mdp6hTRT, conditions = 1))/length(reQTL.index.mdp6h) * 100,2)`% [15%] mdp 6h reQTLs are stimulus specific compared with lps 6h, `r round(length(get_significant_results(resEE.mdp6hTRT, conditions = 2))/length(reQTL.index.mdp6h) * 100,2)`% [13%] mdp 6h reQTLs are stimulus specific compared with rna 6h.

### MDP 90
```{r, echo=FALSE}
reQTL.index.mdp90 = get_significant_results(resEE.mdp90)
A.mdp90TRT = rbind(c(0,0,-1,0,1,0,0),
                   c(0,0,0,0,1,0,-1))
row.names(A.mdp90TRT) = c('mdp90-lps90', 'mdp90-rna90')
```
```{r, echo=FALSE}
resEE.mdp90TRT = resEE
reQTL.mdp90 = subset.data(eQTL.mdp90, reQTL.index.mdp90)
resEE.mdp90TRT$result = mash_compute_posterior_matrices(resEE, reQTL.mdp90, A=A.mdp90TRT, algorithm.version = 'R')
saveRDS(resEE.mdp90TRT, 
        paste0('../output/ImmuneEE.V',vhat,'.center.resEE.mdp90TRT.K',K,'.P',P,'.rds'))

```

```{r}
resEE.mdp90TRT = readRDS(paste0('../output/ImmuneEE.V',vhat,'.center.resEE.mdp90TRT.K',K,'.P',P,'.rds'))
length(get_significant_results(resEE.mdp90TRT))
```

We found `r round(length(get_significant_results(resEE.mdp90TRT, conditions = 1))/length(reQTL.index.mdp90) * 100,2)`% [15%] mdp 90min reQTLs are stimulus specific compared with lps 90min, `r round(length(get_significant_results(resEE.mdp90TRT, conditions = 2))/length(reQTL.index.mdp90) * 100,2)`% [46%] mdp 90min reQTLs are stimulus specific compared with rna 90min.

### RNA 6h
```{r, echo=FALSE}
reQTL.index.rna6h = get_significant_results(resEE.rna6h)
A.rna6hTRT = rbind(c(0,-1,0,0,0,1,0),
                   c(0,0,0,-1,0,1,0))
row.names(A.rna6hTRT) = c('rna6h-lps6h', 'rna6h-mdp6h')
```
```{r, echo=FALSE}
resEE.rna6hTRT = resEE
reQTL.rna6h = subset.data(eQTL.rna6h, reQTL.index.rna6h)
resEE.rna6hTRT$result = mash_compute_posterior_matrices(resEE, reQTL.rna6h, A=A.rna6hTRT, algorithm.version = 'R')
saveRDS(resEE.rna6hTRT, 
        paste0('../output/ImmuneEE.V',vhat,'.center.resEE.rna6hTRT.K',K,'.P',P,'.rds'))

```

```{r}
resEE.rna6hTRT = readRDS(paste0('../output/ImmuneEE.V',vhat,'.center.resEE.rna6hTRT.K',K,'.P',P,'.rds'))
length(get_significant_results(resEE.rna6hTRT))
```

We found `r round(length(get_significant_results(resEE.rna6hTRT, conditions = 1))/length(reQTL.index.rna6h) * 100,2)`% [21%] rna 6h reQTLs are stimulus specific compared with lps 6h, `r round(length(get_significant_results(resEE.rna6hTRT, conditions = 2))/length(reQTL.index.rna6h) * 100,2)`% [45%] rna 6h reQTLs are stimulus specific compared with mdp 6h.

### RNA 90
```{r, echo=FALSE}
reQTL.index.rna90 = get_significant_results(resEE.rna90)
A.rna90TRT = rbind(c(0,0,-1,0,0,0,1),
                   c(0,0,0,0,-1,0,1))
row.names(A.rna90TRT) = c('rna90-lps90', 'rna90-mdp90')
```
```{r, echo=FALSE}
resEE.rna90TRT = resEE
reQTL.rna90 = subset.data(eQTL.rna90, reQTL.index.rna90)
resEE.rna90TRT$result = mash_compute_posterior_matrices(resEE, reQTL.rna90, A=A.rna90TRT, algorithm.version = 'R')
saveRDS(resEE.rna90TRT, 
        paste0('../output/ImmuneEE.V',vhat,'.center.resEE.rna90TRT.K',K,'.P',P,'.rds'))

```

```{r}
resEE.rna90TRT = readRDS(paste0('../output/ImmuneEE.V',vhat,'.center.resEE.rna90TRT.K',K,'.P',P,'.rds'))
length(get_significant_results(resEE.rna90TRT))
```

We found `r round(length(get_significant_results(resEE.rna90TRT, conditions = 1))/length(reQTL.index.rna90) * 100,2)`% [38%] rna 90min reQTLs are stimulus specific compared with lps 90min, `r round(length(get_significant_results(resEE.rna90TRT, conditions = 2))/length(reQTL.index.rna90) * 100,2)`% [29%] rna 90min reQTLs are stimulus specific compared with mdp 90min.

## Time point specificity of reQTLs

### LPS 6h
```{r}
A.lps6hTime = rbind(c(0,1,-1,0,0,0,0))
row.names(A.lps6hTime) = c('lps6h-lps90')
```
```{r}
resEE.lps6hTime = resEE
resEE.lps6hTime$result = mash_compute_posterior_matrices(resEE, reQTL.lps6h , A=A.lps6hTime, algorithm.version = 'R')
saveRDS(resEE.lps6hTime, 
        paste0('../output/ImmuneEE.V',vhat,'.center.resEE.lps6hTime.K',K,'.P',P,'.rds'))

```

```{r}
resEE.lps6hTime = readRDS(paste0('../output/ImmuneEE.V',vhat,'.center.resEE.lps6hTime.K',K,'.P',P,'.rds'))
length(get_significant_results(resEE.lps6hTime))
```

We found `r round(length(get_significant_results(resEE.lps6hTime, conditions = 1))/length(reQTL.index.lps6h) * 100,2)`% [45%] lps6h reQTLs are time point specific compared with lps90min.

### LPS 90
```{r, echo=FALSE}
A.lps90Time = rbind(c(0,-1,1,0,0,0,0))
row.names(A.lps90Time) = c('lps90-lps6h')
```
```{r, echo=FALSE}
resEE.lps90Time = resEE
resEE.lps90Time$result = mash_compute_posterior_matrices(resEE, reQTL.lps90, A=A.lps90Time, algorithm.version = 'R')
saveRDS(resEE.lps90Time, 
        paste0('../output/ImmuneEE.V',vhat,'.center.resEE.lps90Time.K',K,'.P',P,'.rds'))

```

```{r}
resEE.lps90Time = readRDS(paste0('../output/ImmuneEE.V',vhat,'.center.resEE.lps90Time.K',K,'.P',P,'.rds'))
length(get_significant_results(resEE.lps90Time))
```

We found `r round(length(get_significant_results(resEE.lps90Time, conditions = 1))/length(reQTL.index.lps90) * 100,2)`% [36%] lps 90min reQTLs are time point specific compared with lps6h.

### MDP 6h
```{r, echo=FALSE}
A.mdp6hTime = rbind(c(0,0,0,1,-1,0,0))
row.names(A.mdp6hTime) = c('mdp6h-mdp90')
```
```{r, echo=FALSE}
resEE.mdp6hTime = resEE
resEE.mdp6hTime$result = mash_compute_posterior_matrices(resEE, reQTL.mdp6h, A=A.mdp6hTime, algorithm.version = 'R')
saveRDS(resEE.mdp6hTime, 
        paste0('../output/ImmuneEE.V',vhat,'.center.resEE.mdp6hTime.K',K,'.P',P,'.rds'))

```

```{r}
resEE.mdp6hTime = readRDS(paste0('../output/ImmuneEE.V',vhat,'.center.resEE.mdp6hTime.K',K,'.P',P,'.rds'))
length(get_significant_results(resEE.mdp6hTime))
```

We found `r round(length(get_significant_results(resEE.mdp6hTRT, conditions = 1))/length(reQTL.index.mdp6h) * 100,2)`% [40%] mdp 6h reQTLs are time point specific compared with mdp 90min.

### MDP 90
```{r, echo=FALSE}
A.mdp90Time = rbind(c(0,0,0,-1,1,0,0))
row.names(A.mdp90Time) = c('mdp90-mdp6h')
```
```{r, echo=FALSE}
resEE.mdp90Time = resEE
resEE.mdp90Time$result = mash_compute_posterior_matrices(resEE, reQTL.mdp90, A=A.mdp90Time, algorithm.version = 'R')
saveRDS(resEE.mdp90Time, 
        paste0('../output/ImmuneEE.V',vhat,'.center.resEE.mdp90Time.K',K,'.P',P,'.rds'))

```

```{r}
resEE.mdp90Time = readRDS(paste0('../output/ImmuneEE.V',vhat,'.center.resEE.mdp90Time.K',K,'.P',P,'.rds'))
length(get_significant_results(resEE.mdp90Time))
```

We found `r round(length(get_significant_results(resEE.mdp90Time, conditions = 1))/length(reQTL.index.mdp90) * 100,2)`% [38%] mdp 90min reQTLs time point specific compared with mdp 6h.

### RNA 6h
```{r, echo=FALSE}
A.rna6hTime = rbind(c(0,0,0,0,0,1,-1))
row.names(A.rna6hTime) = c('rna6h-rna90')
```
```{r, echo=FALSE}
resEE.rna6hTime = resEE
resEE.rna6hTime$result = mash_compute_posterior_matrices(resEE, reQTL.rna6h, A=A.rna6hTime, algorithm.version = 'R')
saveRDS(resEE.rna6hTime, 
        paste0('../output/ImmuneEE.V',vhat,'.center.resEE.rna6hTime.K',K,'.P',P,'.rds'))

```

```{r}
resEE.rna6hTime = readRDS(paste0('../output/ImmuneEE.V',vhat,'.center.resEE.rna6hTime.K',K,'.P',P,'.rds'))
length(get_significant_results(resEE.rna6hTime))
```

We found `r round(length(get_significant_results(resEE.rna6hTime, conditions = 1))/length(reQTL.index.rna6h) * 100,2)`% [64%] rna 6h reQTLs are time point specific compared with rna 90min.

### RNA 90
```{r, echo=FALSE}
A.rna90Time = rbind(c(0,0,0,0,0,-1,1))
row.names(A.rna90Time) = c('rna90-rna6h')
```
```{r, echo=FALSE}
resEE.rna90Time = resEE
resEE.rna90Time$result = mash_compute_posterior_matrices(resEE, reQTL.rna90, A=A.rna90Time, algorithm.version = 'R')
saveRDS(resEE.rna90Time, 
        paste0('../output/ImmuneEE.V',vhat,'.center.resEE.rna90Time.K',K,'.P',P,'.rds'))

```

```{r}
resEE.rna90Time = readRDS(paste0('../output/ImmuneEE.V',vhat,'.center.resEE.rna90Time.K',K,'.P',P,'.rds'))
length(get_significant_results(resEE.rna90Time))
```

We found `r round(length(get_significant_results(resEE.rna90Time, conditions = 1))/length(reQTL.index.rna90) * 100,2)`% [32%] rna 90min reQTLs are time point specific compared with rna 6h.

<!---
```{r}
get_reQTL_cond = function(m, cond, factor = 0.5, lfsr_thresh = 0.05, FUN = identity){
  condsig = get_significant_results(m, conditions = cond, thresh = lfsr_thresh)
  ratio = FUN(get_pm(m)[condsig, 1])/FUN(get_pm(m)[condsig, cond])
  set = ratio <= factor | ratio >= (1/factor)
  return(list(index= condsig[set], 
              prop = mean(set)))
}
```
Using `MASH`, we found `r round(get_reQTL_cond(resEE, 2, FUN=abs)$prop*100,2)`% of lps 6h eQTLs are reQTLs, `r round(get_reQTL_cond(resEE, 3, FUN=abs)$prop*100,2)`% of lps90 eQTLs are reQTLs, `r round(get_reQTL_cond(resEE, 4, FUN=abs)$prop*100,2)`% of mdp6h eQTLs are reQTLs, `r round(get_reQTL_cond(resEE, 5, FUN=abs)$prop*100,2)`% of mdp90 eQTLs are reQTLs, `r round(get_reQTL_cond(resEE, 6, FUN=abs)$prop*100,2)`% of rna6h eQTLs are reQTLs, `r round(get_reQTL_cond(resEE, 7, FUN=abs)$prop*100,2)`% of rna90 eQTLs are reQTLs. Here, the proportion of reQTLs is estimated by the proportion of significant eQTLs that does not share magnitude with control.

In the paper, they found 3-18% of cis eQTLs in each condition are reQTLs. 

### Treatment specificity of reQTLs
```{r}
get_pairwise_not_sharing_reQTL = function(m, cond1, cond2, factor = 0.5, lfsr_thresh = 0.05, FUN=identity){
  cond1_reQTL_index = get_reQTL_cond(m, cond1, factor = factor, lfsr_thresh = lfsr_thresh, FUN = FUN)$index
  
  ratio = FUN(get_pm(m)[cond1_reQTL_index, cond1])/FUN(get_pm(m)[cond1_reQTL_index, cond2])
  
  return(mean(ratio <= factor | ratio >= (1/factor)))
}
```

Using `MASH`, 

* LPS 90
    + `r round(get_pairwise_not_sharing_reQTL(resEE, 3,5, FUN = abs)*100,2)`% [14%] lps90min reQTLs are stimulus specific compared with mdp90min
    + `r round(get_pairwise_not_sharing_reQTL(resEE, 3,7, FUN = abs)*100,2)`% [51%] lps90min reQTLs are stimulus specific compared with rna90min
* MDP 90
    + `r round(get_pairwise_not_sharing_reQTL(resEE, 5,3, FUN = abs)*100,2)`% [15%] mdp90min reQTLs are stimulus specific compared with lps90min
    + `r round(get_pairwise_not_sharing_reQTL(resEE, 5,7, FUN = abs)*100,2)`% [46%] mdp90min reQTLs are stimulus specific compared with rna90min
* RNA 90
    + `r round(get_pairwise_not_sharing_reQTL(resEE, 7,3, FUN = abs)*100,2)`% [38%] rna90min reQTLs are stimulus specific compared with lps90min
    + `r round(get_pairwise_not_sharing_reQTL(resEE, 7,5, FUN = abs)*100,2)`% [29%] rna90min reQTLs are stimulus specific compared with mdp90min
* LPS 6h
    + `r round(get_pairwise_not_sharing_reQTL(resEE, 2,4, FUN = abs)*100,2)`% [32%] lps6h reQTLs are stimulus specific compared with mdp6h
    + `r round(get_pairwise_not_sharing_reQTL(resEE, 2,6, FUN = abs)*100,2)`% [34%] lps6h reQTLs are stimulus specific compared with rna6h
* MDP 6h
    + `r round(get_pairwise_not_sharing_reQTL(resEE, 4,2, FUN = abs)*100,2)`% [15%] mdp6h reQTLs are stimulus specific compared with lps6h
    + `r round(get_pairwise_not_sharing_reQTL(resEE, 4,6, FUN = abs)*100,2)`% [13%] mdp6h reQTLs are stimulus specific compared with rna6h
* RNA 6h
    + `r round(get_pairwise_not_sharing_reQTL(resEE, 6,2, FUN = abs)*100,2)`% [21%] rna6h reQTLs are stimulus specific compared with lps6h
    + `r round(get_pairwise_not_sharing_reQTL(resEE, 6,4, FUN = abs)*100,2)`% [45%] rna6h reQTLs are stimulus specific compared with mdp6h.

The numbers in '[]' are results from paper.

### Time point specificity of reQTLs
Using `MASH`, 

* LPS
    + `r round(get_pairwise_not_sharing_reQTL(resEE, 3,2, FUN = abs)*100,2)`% [36%] lps90min reQTLs are time point specific compared with lps6h
    + `r round(get_pairwise_not_sharing_reQTL(resEE, 2,3, FUN = abs)*100,2)`% [45%] lps6h reQTLs are time point specific compared with lps90min
* MDP
    + `r round(get_pairwise_not_sharing_reQTL(resEE, 5,4, FUN = abs)*100,2)`% [32%] mdp90min reQTLs are time point specific compared with mdp6h
    + `r round(get_pairwise_not_sharing_reQTL(resEE, 4,5, FUN = abs)*100,2)`% [64%] mdp6h reQTLs are time point specific compared with mdp90min
* RNA
    + `r round(get_pairwise_not_sharing_reQTL(resEE, 7,6, FUN = abs)*100,2)`% [38%] rna90min reQTLs are time point specific compared with rna6h
    + `r round(get_pairwise_not_sharing_reQTL(resEE, 6,7, FUN = abs)*100,2)`% [40%] rna6h reQTLs are time point specific compared with rna90min

The numbers in '[]' are results from paper.
-->

# Session information

<!-- Insert the session information into the document -->
```{r session-info}
```
