---
title: "Immune Interaction"
author: "Yuxin Zou"
date: 2017-12-10
output: html_document
---

```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
```

<!-- Update knitr chunk options -->
```{r knitr-opts-chunk, include=FALSE}
```

<!-- Insert the date the file was last updated -->
```{r last-updated, echo=FALSE, results='asis'}
```

<!-- Insert the code version (Git commit SHA1) if Git repository exists and R
 package git2r is installed -->
```{r code-version, echo=FALSE, results='asis'}
```

# Setup

```{r}
library(mashr)
library(corrplot)
library(dplyr)
data = readRDS('../data/ImmuneQTLSummary.4MASH.rds')
data$max$se = data$max$beta/data$max$z
data$null$se = data$null$beta / data$null$z
```

Posterior:
```{r}
resEZ = readRDS('../output/ImmuneEZ.V1.center.mash_model.K10.P5.rds')
resEZ$result = readRDS('../output/ImmuneEZ.V1.center.mash_posterior.K10.P5.rds')
```

Here is a plot of weights learned.

```{r}
barplot(get_estimated_pi(resEZ), las = 2, cex.names = 0.7)
```

# Qualitative interaction

```{r}
common = Reduce(intersect, list(get_significant_results(resEZ, conditions=1),
                       get_significant_results(resEZ, conditions=2),
                       get_significant_results(resEZ, conditions=3),
                       get_significant_results(resEZ, conditions=4),
                       get_significant_results(resEZ, conditions=5),
                       get_significant_results(resEZ, conditions=6),
                       get_significant_results(resEZ, conditions=7)))
PM.sign = sign(resEZ$result$PosteriorMean[common,])

inter.ind = which(PM.sign - PM.sign[,1] != 0, arr.ind = TRUE)
inter.ind[order(inter.ind[,1]),]
```

Among the eQTLs that significant among all treatments, there are 4 of them have effects in different directions in different conditions.

```{r}
resEZ$result$PosteriorMean[common,][c(3052, 4156, 4303, 4726),]
```
Check the original data:
```{r}
data$max$beta[common, ][c(3052, 4156, 4303, 4726),]
```
According to the thesis, LD among multiple causal SNPs can cause single-SNP analyses to identify eQTL that appear to have strong effects of opposite sign in different tissues. There could be two eQTLs in LD with one another, one of which (A say) has a strong effect in one treatment, and the other of which (B say) has a strong effect in other treatments.

# Session information

<!-- Insert the session information into the document -->
```{r session-info}
```
