---
title: "Immune Data Mash Analysis EZ V1 Loading Results"
author: "Yuxin Zou"
date: 2018-01-04
output: html_document
---

```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
knitr::read_chunk('../code/subset.data.R')
```

<!-- Update knitr chunk options -->
```{r knitr-opts-chunk, include=FALSE}
```

<!-- Insert the date the file was last updated -->
```{r last-updated, echo=FALSE, results='asis'}
```

<!-- Insert the code version (Git commit SHA1) if Git repository exists and R
 package git2r is installed -->
```{r code-version, echo=FALSE, results='asis'}
```

# Set up data
```{r}
library(lattice)
library(ggplot2)
library(colorRamps)
library(mashr)
library(corrplot)
data = readRDS('../data/ImmuneQTLSummary.4MASH.rds')
data$max$se = data$max$beta/data$max$z
data$null$se = data$null$beta / data$null$z

K = 10
P = 5
vhat = 1
```

```{r}
if (vhat == 1) {
  V = cor(data$null$z[which(apply(abs(data$null$z),1, max) < 2),])
} else {
  V = diag(ncol(data$null$z))
}
mash_data = mashr::set_mash_data(Bhat = as.matrix(data$max$beta), 
                                 Shat = as.matrix(data$max$se), 
                                 V = as.matrix(V), 
                                 alpha = 1)
```

# MASH results

```{r}
# EZ
resEZ = readRDS('../output/ImmuneEZ.V1.center.mash_model.Load.K10.P5.rds')
resEZ$result = readRDS('../output/ImmuneEZ.V1.center.mash_posterior.Load.K10.P5.rds')
```

# MASH model fit

The log-likelihood of fit is
```{r} 
get_loglik(resEZ)
```

The log likelihood is slightly higher than the original one [EZ_V1_model](Immune_Data_Mash_V1_EZ_Result.html), which is as we expected. There are more potential covariance structures added in the model.

Here is a plot of weights learned. **The results are similar as before.**

```{r}
options(repr.plot.width=12, repr.plot.height=4)
barplot(get_estimated_pi(resEZ), las = 2, cex.names = 0.7)
```

Most of the mass is on the null, PCA1 and equal effects. `mash` placed `r round(sum(get_estimated_pi(resEZ)[2:14])*100, 4)`% of the mixture components weight on data-driven matrices, `r round(get_estimated_pi(resEZ)['equal_effects']*100,4)`% weight on equal effects matrix.

<!--
* Original estimates
```{r echo=FALSE}
# raw effect
stronggene = data.frame(data$max$beta[2,])
colnames(stronggene) = 'EffectSize'
stronggene$Group = row.names(stronggene)
stronggene$se = data$max$se[2,]
ggplot(stronggene, aes(y = EffectSize, x = Group, color=Group)) + 
  geom_point() + geom_hline(yintercept = 0) + 
  geom_errorbar(aes(ymin=EffectSize-1.96*se, ymax=EffectSize+1.96*se), width=0.4) + 
  theme_bw(base_size=12) + coord_flip() + ggtitle('ILMN_1343295_rs80259531')
```

* `MASH` estimates

```{r echo=FALSE}
# Improved
stronggenePost = data.frame(resEZ$result$PosteriorMean[2,])
colnames(stronggenePost) = 'EffectSize'
stronggenePost$Group = row.names(stronggenePost)
stronggenePost$se = resEZ$result$PosteriorSD[2,]
ggplot(stronggenePost, aes(y = EffectSize, x = Group, color=Group)) + 
  geom_point() + geom_hline(yintercept = 0) + 
  geom_errorbar(aes(ymin=EffectSize-1.96*se, ymax=EffectSize+1.96*se), width=0.4) + 
  theme_bw(base_size=12) + coord_flip() + ggtitle('ILMN_1343295_rs80259531')
```

All estimated effects become similar.
-->

Pairwise sharing

```{r}
x           <- get_pairwise_sharing(resEZ)
colnames(x) <- colnames(get_lfsr(resEZ))
rownames(x) <- colnames(x)
x <- x[rev(rownames(x)),rev(colnames(x))]
x[lower.tri(x)] <- NA
clrs <- colorRampPalette(rev(c("#D73027","#FC8D59","#FEE090","#FFFFBF",
                               "#E0F3F8","#91BFDB","#4575B4")))(64)
n <- nrow(x)
options(repr.plot.width=9, repr.plot.height=9)
print(levelplot(x[n:1,],col.regions = clrs,xlab = "",ylab = "",
                colorkey = TRUE, at = seq(0.7,1,length.out = 64),
                scales = list(cex = 0.5,x = list(rot = 45))))

```

# Compare with original paper

## eQTLs
Among the 21485 top SNPs, `MASH` found `r length(get_significant_results(resEZ))` to be significant in at least one treatment. We refer to these as the 'top eQTLs'.

Using `MASH`, we found `r length(get_significant_results(resEZ, conditions = 1))` genes with an eQTL in control, `r length(get_significant_results(resEZ, conditions = 2))` genes with an eQTL in lps6h, `r length(get_significant_results(resEZ, conditions = 3))` genes with an eQTL in lps90, `r length(get_significant_results(resEZ, conditions = 4))` genes with an eQTL in mdp6h, `r length(get_significant_results(resEZ, conditions = 5))` genes with an eQTL in mdp90, `r length(get_significant_results(resEZ, conditions = 6))` genes with an eQTL in rna6h, `r length(get_significant_results(resEZ, conditions = 7))` genes with an eQTL in rna90.

In the original paper, they identified 717-1653 genes with an eQTL in each condition. So, we found more genes with an eQTL using `MASH`.

```{r echo=FALSE}
comm = Reduce(intersect, list(get_significant_results(resEZ, conditions=1),
                       get_significant_results(resEZ, conditions=2),
                       get_significant_results(resEZ, conditions=3),
                       get_significant_results(resEZ, conditions=4),
                       get_significant_results(resEZ, conditions=5),
                       get_significant_results(resEZ, conditions=6),
                       get_significant_results(resEZ, conditions=7)))
```

There are `r length(comm)` top eQTLs with significant effects among all treatments.

<!---
## Find genes specific to one treatment

```{r}
# function to find gene specific to condition i
Geneto1Cond = function(resEZ, cond){
  conditiontotal = seq(1,ncol(resEZ$result$PosteriorMean))
  OtherCond = conditiontotal[-cond]
  for(i in 1:6){
    if(i == 1){
      setd = setdiff(get_significant_results(resEZ, conditions=cond), 
                     get_significant_results(resEZ, conditions=OtherCond[i]))
    }
    else{
      setd = setdiff(setd,
                     get_significant_results(resEZ, conditions=OtherCond[i]))
    }
    
  }
  return(setd)
}
```

```{r}
GeneNames = row.names(data$max$beta)
for(i in 1:7){
  cat('Gene has significant effect only in condition ', i, ': Total = ', length(GeneNames[Geneto1Cond(resEZ,i)]), '\n', GeneNames[Geneto1Cond(resEZ,i)], '\n')
  cat('\n')
}
```
-->



# Session information

<!-- Insert the session information into the document -->
```{r session-info}
```
