---
title: "Immune_Data_Mash_V1_EZ_loading"
author: "Yuxin Zou"
date: 2018-01-04
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
```

<!-- Update knitr chunk options -->
```{r knitr-opts-chunk, include=FALSE}
```

<!-- Insert the date the file was last updated -->
```{r last-updated, echo=FALSE, results='asis'}
```

<!-- Insert the code version (Git commit SHA1) if Git repository exists and R
 package git2r is installed -->
```{r code-version, echo=FALSE, results='asis'}
```

```{r, echo=FALSE}
# TEMPORARY.
knitr::opts_chunk$set(eval = TRUE)
```

# Set up the data

```{r}
# Load required packages
library(mashr); library(ExtremeDeconvolution); library(flashr2)
```
```{r}
# read data
data = readRDS('../data/ImmuneQTLSummary.4MASH.rds')
data$max$se = data$max$beta/data$max$z
data$null$se = data$null$beta / data$null$z

# set parameters
K = 10
P = 5
vhat = 1
```

# Fit `mash` model

Using a random null set, the cell below computes the weights for input covariance matrices ([Covariance matrices plus loading](Immune_Cov_EZ_Load.html)) in MASH mixture. The output contains matrix of log-likelihoods as well as weights learned from the hierarchical model.

```{r}
if (vhat == 1) {
  V = cor(data$null$z[which(apply(abs(data$null$z),1, max) < 2),])
} else {
  V = diag(ncol(data$null$z))
}

mash_data = mashr::set_mash_data(Bhat = as.matrix(data$null$beta), 
                                 Shat = as.matrix(data$null$se), 
                                 V=as.matrix(V), alpha=1)

Ulist = readRDS('../output/ImmuneEZ.U.center.xtx.Load.K10.P5.rds')$Ulist

saveRDS(mashr::mash(mash_data, Ulist, outputlevel = 1), 
        paste0('../output/ImmuneEZ.V',vhat,'.center.mash_model.Load.K',K,'.P',P,'.rds'))

```

# Posterior inference
Applying hyperparameters learned from the training (the null) set to the test (the top eQTL) set, the cell below computes posterior quantities.

```{r}
U.m = readRDS('../output/ImmuneEZ.V1.center.mash_model.Load.K10.P5.rds')

if (vhat == 1) {
  V = cor(data$null$z[which(apply(abs(data$null$z),1, max) < 2),])
} else {
  V = diag(ncol(data$null$z))
}

mash_data = mashr::set_mash_data(Bhat = as.matrix(data$max$beta), 
                                 Shat = as.matrix(data$max$se), 
                                 V = as.matrix(V), 
                                 alpha = 1)
```

```{r}
saveRDS(mash_compute_posterior_matrices(U.m, mash_data), 
        paste0('../output/ImmuneEZ.V',vhat,'.center.mash_posterior.Load.K',K,'.P',P,'.rds'))

```

# Session information

<!-- Insert the session information into the document -->
```{r session-info}
```
