---
title: "Immune Posterior Check"
author: "Yuxin Zou"
date: 2017-12-04
output: html_document
---

```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
```

<!-- Update knitr chunk options -->
```{r knitr-opts-chunk, include=FALSE}
```

<!-- Insert the date the file was last updated -->
```{r last-updated, echo=FALSE, results='asis'}
```

<!-- Insert the code version (Git commit SHA1) if Git repository exists and R
 package git2r is installed -->
```{r code-version, echo=FALSE, results='asis'}
```

# Setup

```{r}
library(mashr)
library(corrplot)
library(dplyr)
library(stringr)
source('~/Documents/GitHub/mashr-stephens/R/likelihoods_scaleddata.R')
source('~/Documents/GitHub/mashr-stephens/R/RcppExports.R')
source('~/Documents/GitHub/mashr-stephens/R/set_data.R')
source('~/Documents/GitHub/mashr-stephens/R/posterior.R')
source('~/Documents/GitHub/mashr-stephens/R/posterior_common_cov.R')
source('~/Documents/GitHub/mashr-stephens/R/posterior_lowmem.R')
```

Let `mash_posterior` function returns posterior weights as well:

```{r}
mash_compute_posterior_matrices_weights = function(g, data, pi_thresh = 1e-10, algorithm.version = c("Rcpp", "R"), A=NULL ){
  if (!is.null(A) && algorithm.version=='Rcpp'){
    stop("FIXME: not implemented")
  }

  if(class(g)=="mash"){
    alpha = g$alpha
    g = g$fitted_g
    if(alpha != data$alpha){
      stop('The alpha in data is not the one used to compute the mash model.')
    }
  }
  else{
    message('Warning: Please make sure the alpha in data is consistent with the `alpha` used to compute the fitted_g.')
  }

  xUlist = expand_cov(g$Ulist,g$grid,g$usepointmass)
  lm_res = calc_relative_lik_matrix(data, xUlist)
  which.comp = (g$pi > pi_thresh)
  posterior_weights = compute_posterior_weights(g$pi[which.comp], lm_res$lik_matrix[,which.comp])
  posterior_matrices = compute_posterior_matrices(data, xUlist[which.comp],
                                                  posterior_weights,
                                                  algorithm.version, A=A)

  if ((!all(data$Shat_alpha == 1)) && (algorithm.version=='Rcpp')) {
    message("FIXME: 'compute_posterior_matrices' in Rcpp does not transfer EZ to EE")
    ## Recover the scale of posterior(Bhat)
    posterior_matrices$PosteriorMean = posterior_matrices$PosteriorMean * data$Shat_alpha
    posterior_matrices$PosteriorSD = posterior_matrices$PosteriorSD * data$Shat_alpha
  }
  return(list(posterior_weights = posterior_weights,
              posterior_matrices = posterior_matrices))
}
```

# Simulated data

## Shat equal data R = 5

* Fit `mash` model based on `data` $\rightarrow$ estimated weights $\pi$
* Obtain posterior mean for `data` using the `mash` model $\rightarrow$ posterior weights for the covariance structures
* Check whether the posterior weights for the covariance structures are similar as in `mash` model.

`mash` model:

```{r}
set.seed(1)
simdata.equal = simple_sims(500,5,0.5)

# set mash data
TestdataZ.equal = set_mash_data(simdata.equal$Bhat, simdata.equal$Shat, alpha=1)

# center
TestdataZ.equal.center = set_mash_data(apply(as.matrix(TestdataZ.equal$Bhat), 2, function(x) x - mean(x)))

# canonical cov
U.c.equal = cov_canonical(TestdataZ.equal)

# data_driven
m.1by1.Z.equal = mash_1by1(TestdataZ.equal, alpha=1)
strong.Z.equal = get_significant_results(m.1by1.Z.equal,0.05)
U.pca.Z.equal = cov_pca(TestdataZ.equal.center,5,strong.Z.equal)

U.ed.Z.equal = cov_ed(TestdataZ.equal, U.pca.Z.equal, strong.Z.equal)

U.m.Z.equal = mash(TestdataZ.equal, c(U.c.equal, U.ed.Z.equal))
barplot(get_estimated_pi(U.m.Z.equal), las = 2, cex.names = 0.7, main='EZ')
```

Posterior:

```{r}
Post = mash_compute_posterior_matrices_weights(U.m.Z.equal, TestdataZ.equal)
U.m.Z.equal$result = Post$posterior_matrices
posterior_weights = Post$posterior_weights
```

For every sample, the posterior weights for the covariance structures:

```{r}
Weight = matrix(0,nrow=nrow(U.m.Z.equal$result$PosteriorMean),17)
Weight[,1] = posterior_weights[,1]

ind = as.logical(str_count(colnames(posterior_weights), "ED_PCA_1"))
Weight[,2] = apply(posterior_weights[,ind, drop=FALSE], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "ED_PCA_2"))
Weight[,3] = apply(posterior_weights[,ind, drop=FALSE], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "ED_PCA_3"))
Weight[,4] = apply(posterior_weights[,ind, drop=FALSE], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "ED_PCA_4"))
Weight[,5] = apply(posterior_weights[,ind, drop=FALSE], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "ED_PCA_5"))
Weight[,6] = apply(posterior_weights[,ind, drop=FALSE], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "ED_tPCA"))
Weight[,7] = apply(posterior_weights[,ind, drop=FALSE], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "identity"))
Weight[,8] = apply(posterior_weights[,ind, drop=FALSE], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "condition_1"))
Weight[,9] = apply(posterior_weights[,ind, drop=FALSE], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "condition_2"))
Weight[,10] = apply(posterior_weights[,ind, drop=FALSE], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "condition_3"))
Weight[,11] = apply(posterior_weights[,ind, drop=FALSE], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "condition_4"))
Weight[,12] = apply(posterior_weights[,ind, drop=FALSE], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "condition_5"))
Weight[,13] = apply(posterior_weights[,ind, drop=FALSE], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "equal_effects"))
Weight[,14] = apply(posterior_weights[,ind, drop=FALSE], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "simple_het_1"))
Weight[,15] = apply(posterior_weights[,ind, drop=FALSE], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "simple_het_2"))
Weight[,16] = apply(posterior_weights[,ind, drop=FALSE], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "simple_het_3"))
Weight[,17] = apply(posterior_weights[,ind, drop=FALSE], 1, sum)

colnames(Weight) = c('null', 'ED_PCA_1','ED_PCA_2','ED_PCA_3','ED_PCA_4','ED_PCA_5','ED_tPCA',
                     'identity','condition_1', 'condition_2','condition_3','condition_4','condition_5',
                     'equal_effects', 'simple_het_1', 'simple_het_2', 'simple_het_3')
row.names(Weight) = row.names(U.m.Z.equal$result$PosteriorMean)
```

Identify the covariance structure with the max posterior weight for each sample:

```{r}
Freqe = apply(Weight,1, which.max)

Da = data.frame(id = 1:length(Freqe), Freq = Freqe)
Da_summary = Da %>% group_by(Freq) %>% summarise(Total=n())
x = Da_summary$Total
names(x) = colnames(Weight)[Da_summary$Freq]
barplot(x, las = 2, cex.names = 0.7)
```

The posterior weights for the covariance structures have similar pattern to the weights in `mash` model.

# Simulate Shat different among samples, same among conditions

```{r}
set.seed(1)
simdata.diff = simple_sims(500, 5, rep(c(0.5,0.4,5,1,1), 400))
simdata.diff$z = simdata.diff$Bhat/simdata.diff$Shat
# set mash data
TestdataBeta.diff = set_mash_data(Bhat=simdata.diff$Bhat,
                               Shat=simdata.diff$Shat, 
                               alpha = 0)
# Create covariance matrices
# center
TestdataZ.diff.center = set_mash_data(Bhat = apply(as.matrix(simdata.diff$z), 2, function(x) x - mean(x)), alpha=0)

# canonical cov
U.c.diff = cov_canonical(TestdataZ.diff.center)

# data_driven
m.1by1.Z.diff = mash_1by1(TestdataBeta.diff, alpha=1)
strong.Z.diff = get_significant_results(m.1by1.Z.diff,0.05)
U.pca.Z.diff = cov_pca(TestdataZ.diff.center,5,strong.Z.diff)

U.ed.beta.diff = cov_ed(TestdataBeta.diff, U.pca.Z.diff, strong.Z.diff)
U.m.beta.diff = mash(TestdataBeta.diff, c(U.c.diff, U.ed.beta.diff))

barplot(get_estimated_pi(U.m.beta.diff), las = 2, cex.names = 0.7, main='EE')
```

```{r}
Post = mash_compute_posterior_matrices_weights(U.m.beta.diff, TestdataBeta.diff)
U.m.beta.diff$result = Post$posterior_matrices
posterior_weights = Post$posterior_weights
```

```{r echo=FALSE}
Weight = matrix(0,nrow=nrow(U.m.beta.diff$result$PosteriorMean),17)
Weight[,1] = posterior_weights[,1]

ind = as.logical(str_count(colnames(posterior_weights), "ED_PCA_1"))
Weight[,2] = apply(posterior_weights[,ind, drop=FALSE], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "ED_PCA_2"))
Weight[,3] = apply(posterior_weights[,ind, drop=FALSE], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "ED_PCA_3"))
Weight[,4] = apply(posterior_weights[,ind, drop=FALSE], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "ED_PCA_4"))
Weight[,5] = apply(posterior_weights[,ind, drop=FALSE], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "ED_PCA_5"))
Weight[,6] = apply(posterior_weights[,ind, drop=FALSE], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "ED_tPCA"))
Weight[,7] = apply(posterior_weights[,ind, drop=FALSE], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "identity"))
Weight[,8] = apply(posterior_weights[,ind, drop=FALSE], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "condition_1"))
Weight[,9] = apply(posterior_weights[,ind, drop=FALSE], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "condition_2"))
Weight[,10] = apply(posterior_weights[,ind, drop=FALSE], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "condition_3"))
Weight[,11] = apply(posterior_weights[,ind, drop=FALSE], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "condition_4"))
Weight[,12] = apply(posterior_weights[,ind, drop=FALSE], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "condition_5"))
Weight[,13] = apply(posterior_weights[,ind, drop=FALSE], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "equal_effects"))
Weight[,14] = apply(posterior_weights[,ind, drop=FALSE], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "simple_het_1"))
Weight[,15] = apply(posterior_weights[,ind, drop=FALSE], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "simple_het_2"))
Weight[,16] = apply(posterior_weights[,ind, drop=FALSE], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "simple_het_3"))
Weight[,17] = apply(posterior_weights[,ind, drop=FALSE], 1, sum)

colnames(Weight) = c('null', 'ED_PCA_1','ED_PCA_2','ED_PCA_3','ED_PCA_4','ED_PCA_5','ED_tPCA',
                     'identity','condition_1', 'condition_2','condition_3','condition_4','condition_5',
                     'equal_effects', 'simple_het_1', 'simple_het_2', 'simple_het_3')
row.names(Weight) = row.names(U.m.beta.diff$result$PosteriorMean)
```

```{r}
Freqe = apply(Weight,1, which.max)

Da = data.frame(id = 1:length(Freqe), Freq = Freqe)
Da_summary = Da %>% group_by(Freq) %>% summarise(Total=n())
x = Da_summary$Total
names(x) = colnames(Weight)[Da_summary$Freq]
barplot(x, las = 2, cex.names = 0.7)
```

The posterior weights for the covariance structures have similar pattern to the weights in `mash` model.


# Immune Data

* Fit `mash` model based on `null data` $\rightarrow$ estimated weights $\pi$
* Obtain posterior mean for `null data` using the `mash` model $\rightarrow$ posterior weights for the covariance structures; Obtain posterior mean for `max data` using the `mash` model $\rightarrow$ posterior weights for the covariance structures
* Check whether the posterior weights for the covariance structures are similar as in `mash` model.

```{r}
data = readRDS('~/Documents/GitHub/mash-application-immune/data/ImmuneQTLSummary.4MASH.rds')
data$max$se = data$max$beta/data$max$z
data$null$se = data$null$beta / data$null$z

V = cor(data$null$z[which(apply(abs(data$null$z),1, max) < 2),])
```

## Posterior on null set

```{r}
mash_data = set_mash_data(Bhat = data$null$beta,
                          Shat = data$null$se,
                          alpha=1,
                          V = V)

resEZ = readRDS('~/Documents/GitHub/mash-application-immune/output/ImmuneEZ.V1.center.mash_model.K10.P5.rds')
Post = mash_compute_posterior_matrices_weights(resEZ, mash_data)
resEZ$result = Post$posterior_matrices
posterior_weights = Post$posterior_weights
barplot(get_estimated_pi(resEZ), las = 2, cex.names = 0.7)
```

```{r echo=FALSE}
Weight = matrix(0,nrow=nrow(resEZ$result$PosteriorMean),26)
Weight[,1] = posterior_weights[,1]

ind = as.logical(str_count(colnames(posterior_weights), "ED_Flash_1"))
Weight[,2] = apply(posterior_weights[,ind], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "ED_Flash_2"))
Weight[,3] = apply(posterior_weights[,ind], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "ED_Flash_3"))
Weight[,4] = apply(posterior_weights[,ind], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "ED_Flash_4"))
Weight[,5] = apply(posterior_weights[,ind], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "ED_Flash_5"))
Weight[,6] = apply(posterior_weights[,ind], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "ED_tFlash"))
Weight[,7] = apply(posterior_weights[,ind], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "ED_PCA_1"))
Weight[,8] = apply(posterior_weights[,ind], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "ED_PCA_2"))
Weight[,9] = apply(posterior_weights[,ind], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "ED_PCA_3"))
Weight[,10] = apply(posterior_weights[,ind], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "ED_PCA_4"))
Weight[,11] = apply(posterior_weights[,ind], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "ED_PCA_5"))
Weight[,12] = apply(posterior_weights[,ind], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "ED_tPCA"))
Weight[,13] = apply(posterior_weights[,ind], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "ED_XX"))
Weight[,14] = apply(posterior_weights[,ind], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "identity"))
Weight[,15] = apply(posterior_weights[,ind], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "ctrl"))
Weight[,16] = apply(posterior_weights[,ind], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "lps6h"))
Weight[,17] = apply(posterior_weights[,ind], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "lps90"))
Weight[,18] = apply(posterior_weights[,ind], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "mdp6h"))
Weight[,19] = apply(posterior_weights[,ind], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "mdp90"))
Weight[,20] = apply(posterior_weights[,ind], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "rna6h"))
Weight[,21] = apply(posterior_weights[,ind], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "rna90"))
Weight[,22] = apply(posterior_weights[,ind], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "equal_effects"))
Weight[,23] = apply(posterior_weights[,ind], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "simple_het_1"))
Weight[,24] = apply(posterior_weights[,ind], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "simple_het_2"))
Weight[,25] = apply(posterior_weights[,ind], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "simple_het_3"))
Weight[,26] = apply(posterior_weights[,ind], 1, sum)

colnames(Weight) = c('null','ED_Flash_1', 'ED_Flash_2', 'ED_Flash_3', 'ED_Flash_4', 'ED_Flash_5', 'ED_tFlash', 'ED_PCA_1','ED_PCA_2','ED_PCA_3','ED_PCA_4','ED_PCA_5','ED_tPCA',
                     'ED_XX','identity','ctrl', 'lps6h','lps90','mdp6h','mdp90',
                     'rna6h', 'rna90','equal_effects', 'simple_het_1', 'simple_het_2', 'simple_het_3')
row.names(Weight) = row.names(resEZ$result$PosteriorMean)
```

```{r}
Freqe = apply(Weight,1, which.max)

Da = data.frame(id = 1:length(Freqe), Freq = Freqe)
Da_summary = Da %>% group_by(Freq) %>% summarise(Total=n())
Da_summary
x = Da_summary$Total
names(x) = colnames(Weight)[Da_summary$Freq]
barplot(x, las = 2, cex.names = 0.7)
```

The number of genes with high posterior weights on `equal_effects` are small.

```{r}
common = Reduce(intersect, list(get_significant_results(resEZ, conditions=1),
                       get_significant_results(resEZ, conditions=2),
                       get_significant_results(resEZ, conditions=3),
                       get_significant_results(resEZ, conditions=4),
                       get_significant_results(resEZ, conditions=5),
                       get_significant_results(resEZ, conditions=6),
                       get_significant_results(resEZ, conditions=7)))
PM.sign = sign(resEZ$result$PosteriorMean[common,])
all(PM.sign - PM.sign[,1] == 0)
```
There is no qualitative interaction cases in the null set.


## Posterior on max set

```{r}
mash_data = set_mash_data(Bhat = data$max$beta,
                          Shat = data$max$se,
                          alpha=1,
                          V = V)
resEZ = readRDS('~/Documents/GitHub/mash-application-immune/output/ImmuneEZ.V1.center.mash_model.K10.P5.rds')
Post = mash_compute_posterior_matrices_weights(resEZ, mash_data)
resEZ$result = Post$posterior_matrices
posterior_weights = Post$posterior_weights
```

```{r echo=FALSE}
Weight = matrix(0,nrow=nrow(resEZ$result$PosteriorMean),26)
Weight[,1] = posterior_weights[,1]

ind = as.logical(str_count(colnames(posterior_weights), "ED_Flash_1"))
Weight[,2] = apply(posterior_weights[,ind], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "ED_Flash_2"))
Weight[,3] = apply(posterior_weights[,ind], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "ED_Flash_3"))
Weight[,4] = apply(posterior_weights[,ind], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "ED_Flash_4"))
Weight[,5] = apply(posterior_weights[,ind], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "ED_Flash_5"))
Weight[,6] = apply(posterior_weights[,ind], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "ED_tFlash"))
Weight[,7] = apply(posterior_weights[,ind], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "ED_PCA_1"))
Weight[,8] = apply(posterior_weights[,ind], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "ED_PCA_2"))
Weight[,9] = apply(posterior_weights[,ind], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "ED_PCA_3"))
Weight[,10] = apply(posterior_weights[,ind], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "ED_PCA_4"))
Weight[,11] = apply(posterior_weights[,ind], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "ED_PCA_5"))
Weight[,12] = apply(posterior_weights[,ind], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "ED_tPCA"))
Weight[,13] = apply(posterior_weights[,ind], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "ED_XX"))
Weight[,14] = apply(posterior_weights[,ind], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "identity"))
Weight[,15] = apply(posterior_weights[,ind], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "ctrl"))
Weight[,16] = apply(posterior_weights[,ind], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "lps6h"))
Weight[,17] = apply(posterior_weights[,ind], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "lps90"))
Weight[,18] = apply(posterior_weights[,ind], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "mdp6h"))
Weight[,19] = apply(posterior_weights[,ind], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "mdp90"))
Weight[,20] = apply(posterior_weights[,ind], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "rna6h"))
Weight[,21] = apply(posterior_weights[,ind], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "rna90"))
Weight[,22] = apply(posterior_weights[,ind], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "equal_effects"))
Weight[,23] = apply(posterior_weights[,ind], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "simple_het_1"))
Weight[,24] = apply(posterior_weights[,ind], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "simple_het_2"))
Weight[,25] = apply(posterior_weights[,ind], 1, sum)
ind = as.logical(str_count(colnames(posterior_weights), "simple_het_3"))
Weight[,26] = apply(posterior_weights[,ind], 1, sum)

colnames(Weight) = c('null','ED_Flash_1', 'ED_Flash_2', 'ED_Flash_3', 'ED_Flash_4', 'ED_Flash_5', 'ED_tFlash', 'ED_PCA_1','ED_PCA_2','ED_PCA_3','ED_PCA_4','ED_PCA_5','ED_tPCA',
                     'ED_XX','identity','ctrl', 'lps6h','lps90','mdp6h','mdp90',
                     'rna6h', 'rna90','equal_effects', 'simple_het_1', 'simple_het_2', 'simple_het_3')
row.names(Weight) = row.names(resEZ$result$PosteriorMean)
```

```{r}
Freqe = apply(Weight,1, which.max)

Da = data.frame(id = 1:length(Freqe), Freq = Freqe)
Da_summary = Da %>% group_by(Freq) %>% summarise(Total=n())
Da_summary
x = Da_summary$Total
names(x) = colnames(Weight)[Da_summary$Freq]
barplot(x, las = 2, cex.names = 0.7)
```

There are some genes with high posterior weights on `ED_tFlash` and `identity`.

Posterior weights for the 4 genes have effects in different directions in different conditions, among the eQTLs that significant among all treatments:

```{r}
common = Reduce(intersect, list(get_significant_results(resEZ, conditions=1),
                       get_significant_results(resEZ, conditions=2),
                       get_significant_results(resEZ, conditions=3),
                       get_significant_results(resEZ, conditions=4),
                       get_significant_results(resEZ, conditions=5),
                       get_significant_results(resEZ, conditions=6),
                       get_significant_results(resEZ, conditions=7)))

par(mfrow=c(2,2))
for(i in c(3052, 4156, 4303, 4726)){
  barplot(Weight[common,][i, ], las = 2, cex.names = 0.7, main=row.names(Weight[common])[i])
}
par(mfrow=c(1,1))
```


# Session information

<!-- Insert the session information into the document -->
```{r session-info}
```
