---
title: "Simple Simulation Example"
author: "Yuxin Zou"
date: '2018-01-10'
output:
  html_document: default
  pdf_document: default
---
```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
```

<!-- Update knitr chunk options -->
```{r knitr-opts-chunk, include=FALSE}
```

<!-- Insert the date the file was last updated -->
```{r last-updated, echo=FALSE, results='asis'}
```

<!-- Insert the R version (Git commit SHA1) if Git repository exists and R
 package git2r is installed -->
```{r R-version, echo=FALSE, results='asis'}
```

```{r, echo=FALSE}
# TEMPORARY.
knitr::opts_chunk$set(eval = TRUE)
```

```{r, echo=FALSE}
library(mashr)
```

# Simulation Design

In the simplest case, there is no true deviation exists.
$$c_{j} = \mu_{j} 1$$
$$\hat{c}_{j} \sim N_{8}(c_{j}, \frac{1}{2}I)$$
Let L be the contrast matrix. Therefore, $$\hat{\delta}_{j} = L\hat{c}_{j} \sim N_{7}(0, \frac{1}{2}LL')$$

We first generate the data:
```{r}
set.seed(1)
data = sim.contrast1(nsamp = 10000, ncond = 8)
```

Set up the contrast matrix and the mash contrast data object
```{r}
L = rbind(c(-1,1,0,0,0,0,0,0),
          c(-1,0,1,0,0,0,0,0),
          c(-1,0,0,1,0,0,0,0),
          c(-1,0,0,0,1,0,0,0),
          c(-1,0,0,0,0,1,0,0),
          c(-1,0,0,0,0,0,1,0),
          c(-1,0,0,0,0,0,0,1))
row.names(L) = c('2-1','3-1','4-1','5-1','6-1','7-1','8-1')
mash_data = mash_set_data(Bhat=data$Chat, Shat=data$Shat)
mash_data_L = mash_set_data_contrast(mash_data, L)
```

Set up the covariance matrices:

There are two types of covariance matrix you can use in mash: “canonical” and “data-driven”. 
```{r}
# canonical
U.c = cov_canonical(mash_data_L)
# data driven
mash_data_L.z = mash_data_L
mash_data_L.z$Bhat = mash_data_L$Bhat/mash_data_L$Shat
m.1by1 = mash_1by1(mash_data_L.z)
strong = get_significant_results(m.1by1,0.05)
# no strong
# no data driven
```

Fit `mashcontrast` model
```{r}
mashcontrast.model = mash(mash_data_L, U.c, algorithm.version = 'R')
```

```{r}
length(get_significant_results(mashcontrast.model))
```
There is no discovery, which is as we expected. The true deviations are zero for all samples.

```{r}
barplot(get_estimated_pi(mashcontrast.model),las = 2, cex.names = 0.7)
```

# Comparing discover result with $\hat{\delta}_{j} \sim N_{7}(0,I)$:
```{r}
Indep.data = mash_set_data(Bhat = data$Chat%*%t(L))
U.c = cov_canonical(Indep.data)
Indep.model = mash(Indep.data, U.c, algorithm.version = 'R')
```
```{r}
length(get_significant_results(Indep.model))
```
There are more false positives.

```{r}
barplot(get_estimated_pi(Indep.model),las = 2,cex.names = 0.7)
```

# Comparing discover result with $\hat{z} \sim N_{7}(0,I)$:

In this case, the observed deviations are truly independent.

```{r}
# simulate true independent delta
D = matrix(0, nrow=10000, ncol = 7)
Shat = matrix(1, nrow=10000, ncol = 7)
set.seed(1)
E = matrix(rnorm(length(Shat), mean=0, sd=Shat), nrow=10000, ncol = 7)
Dhat = D + E
row_ids = paste0("sample_", 1:nrow(D))
col_ids = paste0("condition_", 1:ncol(D))
rownames(D) = row_ids
colnames(D) = col_ids
rownames(Dhat) = row_ids
colnames(Dhat) = col_ids
rownames(Shat) = row_ids
colnames(Shat) = col_ids
```

```{r}
mash_delta = mash_set_data(Bhat = Dhat, Shat = Shat)
U.c = cov_canonical(mash_delta)
mash_delta_model = mash(mash_delta, U.c, algorithm.version = 'R')
```
```{r}
length(get_significant_results(mash_delta_model))
```

```{r}
barplot(get_estimated_pi(mash_delta_model),las = 2,cex.names = 0.7)
```
From the above comparisons, we show that the wrong assumption $\hat{\delta}\sim N_{7}(0,I)$ produces many more false positives.

# Session information

<!-- Insert the session information into the document -->
```{r session-info}
```
